---
title: "Gov 50 Final Project"
author: Alex Heuss
description: "A really good final project. What's it about? Who's to say?"
output:
  distill::distill_article:
    self_contained: false
---


```{r, include = FALSE}
library(tidyverse)
library(ggplot2)


```



## Project thoughts

I'm going into my project with an open mind. I've done some preliminary browsing of data and think I want to explore data related to food or drinks in the United States. I've found good data sets for chain restaurants and Halloween candy, but I'd really like to do some digging to find information about the most popular coffee chains or the history of bubble tea popularity in the United States over time. I'm willing to go with the flow based on the most comprehensive or interesting data set I stumble across, but those are some guiding topics to get me started. 

```{r, include = FALSE}
part_1 <- read_csv("https://raw.githubusercontent.com/friendlycities-gatech/chainness/main/data/chainness_point_2021_part1.csv")


part_2 <- read_csv("https://raw.githubusercontent.com/friendlycities-gatech/chainness/main/data/chainness_point_2021_part2.csv")

part_3 <- read_csv("https://raw.githubusercontent.com/friendlycities-gatech/chainness/main/data/chainness_point_2021_part3.csv")

```

```{r, include = FALSE}
data <- 
  rbind(part_1, part_2, part_3)

```


## Project Proposal

What is the relationship between chain coffee restaurants and college towns? In my project, I hope to explore the location of chain coffee locations across the United States, specifically in relation to college towns. I hypothesize there will be a higher frequency of coffee chains overall in college towns, a positive relationship. My variables of interest are restaurant name, state, county, and city, but my specific explanatory variable will be one that I create called "college_town", which will be marked with a 1 if the town has a four year higher education institution and a 0 if not.  My outcome variable of interest is frequency, as well as mean chain coffee stores in college towns, both measured as a number. My hypotheses would be supported if the frequency of chain coffee stores is higher in college towns than the frequency of chain coffee stores in non-college towns. My hypothesis would not be supported if I were to find a negative or no correlation between chain coffee stores and college towns. My project is based on a database provided by Friendly Cities on GitHub and includes 800,000 restaurants throughout the United States. The "college_town" variable is being created using information found on Campus Explorer. 

```{r, include = FALSE}
data |>
  filter(RestaurantName == "Dunkin")
  
unique(data$UA_NAME)

```

```{r, include = FALSE}
college_towns <- c("Bloomington, MN", "Minneapolis, MN", "Bemidji, MN",  "Mankato, MN", "St. Paul, MN", "Northfield, MN", "St. Joseph, MN", "Saint Joseph, MN", "Moorhead, MN", "Saint Bonifacius, MN", "St. Bonifacous, MN", "St. Peter, MN", "Saint Peter, MN", "St. Louis Park, MN", "Saint Louis Park, MN", "New Ulm, MN", "St. Cloud, MN", "Saint Cloud, MN", "Collegeville, MN", "Winona, MN", "Marshall, MN", "Duluth, MN", "Crookston, MN", "Morris, MN", "Rochester, MN",
  
                   "Alcorn State, MS", "Jackson, MS", "Blue Mountain, MS"," Cleveland, MS", "Clinton, MS", "Mississippi State, MS", "Columbus, MS", "Itta Bena, MS", "Holly Springs, MS", "Laurel, MS", "Tougaloo, MS", "University, MS", "Hattiesburg, MS",
                   
                   "St. Joseph, MO", "Kansas City, MO", "Springfield, MO", "Moberly, MO", "Fayette, MO", "Point Lookout, MO", "Columbia, MO", "Conception, MO", "Nevada, MO"," Canton, MO", "Hannibal, MO", "Jefferson City, MO", "St. Charles, MO", "Chesterfield, MO", "Joplin, MO", "Rolla, MO", "Marshall, MO", "St. Joseph, MO", "Maryville, MO", "Parkville, MO", "Florissant, MO", "Cape Girardeau, MO", "Bolivar, MO", "Fenton, MO", "Kirksville, MO", "Warrensburg, MO", "Wentzville, MO", "Fulton, MO", "Liberty, MO",
                   
                  "Helena, MT", "Bozeman, MT", "Billings, MT", "Havre, MT", "Butte, MT", "Pablo, MT", "Missoula, MT", "Box Elder, MT", "Dillon, MT", "Great Falls, MT",
                  
                  "Bellevue, NE", "Lincoln, NE", "Chadron, NE", "Omaha, NE", "Seward, NE", "Hastings, NE", "Crete, NE", "Fremont, NE", "Papillion, NE", "Peru, NE", "Gering, NE", "Kearney, NE", "Wayne, NE", "York, NE",
                  
                  "Las Vegas, NV", "Henderson, NV", "Elko, NV", "Reno, NV", "Incline Village, NV", "Carson City, NV",
                  
                  "New London, NH", "Hanover, NH", "Rindge, NH", "Concord, NH", "Keene, NH", "Warner, NH", "Henniker, NH", "Plymouth, NH", "Nashua, NH", "Manchester, NH", "Merrimack, NH", "Durham, NH",
                  
                  "Lakewood, NJ", "Woodland Park, NJ", "Bloomfield, NJ", "Caldwell, NJ", "Hackettstown, NJ", "North Brunswick, NJ", "Morristown, NJ", "Madison, NJ", "Belleville, NJ", "Jersey City, NJ", "Ramsey, NJ", "Teaneck, NJ", "Lodi, NJ", "Union, NJ", "West Long Branch, NJ", "Montclair, NJ", "Newark, NJ", "Princeton, NJ", "Edison, NJ", "Mahwah, NJ", "Lawrenceville, NJ", "Glassboro, NJ", "Camden, NJ", "South Orange, NJ", "Hoboken, NJ", "Galloway, NJ", "Cherry Hill, NJ", "Adelphia, NJ", "Ewing, NJ", "Trenton, NJ", "Wayne, NJ", "Keyport, NJ", "North Plainfield, NJ", "Elizabeth, NJ", "Howell, NJ",
                  
                  "Albuquerque, NM", "Portales, NM", "Santa Fe, NM", "Crownpoint, NM", "Las Vegas, NM", "Socorro, NM", "Las Cruces, NM", "Espanola, NM", "Hobbs, NM", "Silver City, NM",
                  
                  "Garden City, NY", "Albany, NY", "Alfred, NY", "New York, NY", "New York City, New York", "Brooklyn, NY", "Monsey, NY", "Annandale-On-Hudson, NY", "Spring Valley, NY", "Far Rockaway, NY", "Vestal, NY", "Buffalo, NY", "Rochester, NY", "Orchard Park, NY", "Liverpool, NY", "Cazenovia, NY", "Potsdam, NY", "Hamilton, NY", "Bronx, NY", "Staten Island, NY", "Bronxville, NY", "Ithaca, NY", "Hyde Park, NY", "Queens, NY", "Jamaica, NY", "Amherst, NY", "Johnson City, NY", "Orangeburg, NY", "Elmira, NY", "Farmingdale, NY", "Dix Hills, NY", "Clinton, NY", "Oneonta, NY", "Hamburg, NY", "Geneva, NY", "Hempstead, NY", "Houghton, NY", "New Rochelle, NY", "Jamestown, NY", "Ossining, NY", "Keuka Park, NY", "Syracuse, NY", "Brookville, NY", "Riverdale, NY", "Purchase, NY", "Poughkeepsie, NY", "Dobbs Ferry, NY", "Rockville Centre, NY", "Newburgh, NY", "Syosset, NY", "Mineola, NY"," Old Westbury, NY", "Niagara University, NY", "Peekskill, NY", "Paul Smiths, NY", "Forest Hills, NY", "Long Beach, NY", "Flushing, NY", "Troy, NY", "Lawrence, NY", "Loudonville, NY", "Saratoga Springs, NY", "St. Bonaventure, NY", "Saint Bonaventure, NY", "Brooklyn Heights, NY", "Canton, NY", "Patchogue, NY", "Sparkill, NY", "New Paltz, NY", "Stony Brook, NY", "Fredonia, NY", "Brockport, NY", "Geneseo, NY", "Oswego, NY", "Plattsburgh, NY", "Potsdam, NY", "Cobleskill, NY", "Delhi, NY", "Cortland, NY", "Throggs Neck, NY", "Morrisville, NY", "Utica, NY", "White Plains, NY", "Schenectady, NY", "Kings Point, NY", "West Point, NY", "Glen Cove, NY", "Aurora, NY", "Mount Kisco, NY", "Greenfield Park, NY", "New Windsor, NY", "Kew Gardens, NY", "Suffern, NY", "Monroe, NY", "South Fallsburg, NY",
                  
                  "Durham, NC", "Boone, NC", "Wilson, NC", "Belmont, NC", "Greensboro, NC", "Brevard, NC", "Concord, NC", "Buies Creek, NC", "Winston Salem, NC", "Fayetteville, NC", "Charlotte, NC", "Salisbury, NC", "Murfreesboro, NC", "Davidson, NC", "Greenville, NC", "Elizabeth City, NC", "Elon, NC", "Boiling Springs, NC", "Dunn, NC", "High Point, NC", "Banner Elk, NC", "Raleigh, NC", "Hickory, NC", "Salisbury, NC", "Mars Hill, NC", "Montreat, NC", "Rocky Mount, NC", "Misenheimer, NC", "Winston-Salem, NC", "Wilmington, NC", "Wake Forest, NC", "Wendell, NC", "Laurinburg, NC", "Morrisville, NC", "Mount Olive, NC", "Asheville, NC", "Chapel Hill, NC", "Pembroke, NC", "Henderson, NC", "Swannanoa, NC", "Cullowhee, NC", "Wingate, NC",
                  
                  "Bismarck, ND", "Dickinson, ND", "Mayville, ND", "Minot, ND", "Fargo, ND", "New Town, ND", "Fort Yates, ND", "Ellendale, ND", "Belcourt, ND", "Jamestown, ND", "Grand Forks, ND", "Valley City, ND",
                  
                  "Salem, OH", "Yellow Springs, OH", "Cincinnati, OH", "Ashland, OH", "Canton, OH", "Berea, OH", "Bluffton, OH", "Huron, OH", "Bowling Green, OH", "Parma, OH", "Columbus, OH", "Cleveland, OH", "Cedarville, OH", "Wilberforce, OH", "Springfield, OH", "Defiance, OH", "Granville, OH", "Steubenville, OH", "Tiffin, OH", "Akron, OH", "Hiram, OH", "Westerville, OH", "University Heights, OH", "Ashtabula, OH", "East Liverpool, OH", "Burton, OH", "Kent, OH", "Warren, OH", "New Philadelphia, OH", "Gambier, OH", "Kettering, OH", "Painesville, OH", "Elyria, OH", "Sylvania, OH", "Marietta, OH", "Toledo, OH", "Hamilton, OH", "Middletown, OH", "Oxford, OH", "Mount Vernon, OH", "New Concord, OH", "Mansfield, OH", "Oberlin, OH", "Circleville, OH", "Ada, OH", "Lima, OH", "Marion, OH", "Newark, OH", "Chillicothe, OH", "Saint Clairesville, OH", "St. Clairesville, OH", "Lancaster, OH", "Athens, OH", "Ironton, OH", "Zanesville, OH", "Delaware, OH", "Wickliffe, OH", "Portsmouth, OH", "Dayton, OH", "Warrensville Heights, OH", "Wooster, OH", "Lakewood, OH", "Findlay, OH", "South Point, OH", "Blue Ash, OH", "Batavia, OH", "Dayton, OH", "Alliance, OH", "Rio Grande, OH", "Pepper Pike, OH", "North Canton, OH", "Wilmington, OH", "Celina, OH", "Youngstown, OH",
                  
                  "Muskogee, OK", "Lawton, OK", "Ada, OK", "Shawnee, OK", "Langston, OK", "Oklahoma City, OK", "Tulsa, OK", "Tahlequah, OK", "Alva, OK", "Edmond, OK", "Goodwell, OK", "Okmulgee, OK", "Stillwater, OK", "Bartlesville, OK", "Moore, OK", "Claremore, OK", "Durant, OK", "Bethany, OK", "Weatherford, OK", "Norman, OK", "Chickasha, OK",
                  
                  "Portland, OR", "Salem, OR", "La Grande, OR", "Newburg, OR", "McMinnville, OR", "Saint Benedict, OR", "St. Benedict, OR", "Eugene, OR", "Klamath Falls, OR", "Corvallis, OR", "Bend, OR", "Forest Grove, OR", "Beaverton, OR", "Ashland, OR", "Monmouth, OR",
                  
                  "Reading, PA", "Meadville, PA", "Glenside, PA", "Bloomsburg, PA", "Bryn Athyn, PA", "Bryn Mawr, PA", "Lewisburg, PA", "Radnor, PA", "Reading, PA", "Meadville, PA", "Glenside, PA", "Bloomsburg, PA", "Bryn Athyn, PA", "Bryn Mawr, PA", "Lewisburg, PA", "Radnor, PA", "Langhorne, PA", "California, PA", "Pittsburgh, PA", "Allentown, PA", "Summerdale, PA", "Philadelphia, PA", "Cheyney, PA", "Clarion, PA", "South Abington Township, PA", "Doylestown, PA", "Center Valley, PA", "Fort Washington, PA", "Ft. Washington, PA", "Carlisle, PA", "East Stroudsburg, PA", "Saint Davids, PA", "St. Davids, PA", "Edinboro, PA", "Elizabethtown, PA", "Lancaster, PA", "Erie, PA", "Beaver Falls, PA", "Gettysburg, PA", "Melrose Park, PA", "Grove City, PA", "Gwynedd Valley, PA", "Harrisburg, PA", "Haverford, PA", "Immaculata, PA", "Indiana, PA", "Huntingdon, PA", "La Plume, PA", "Wilkes Barre, PA", "Kutztown, PA", "Scranton, PA", "Easton, PA", "Annville, PA", "Bethlehem, PA", "Lincoln University, PA", "Lock Haven, PA", "Williamsport, PA", "Jenkintown, PA", "Mansfield, PA", "Mechanicsburg, PA", "MIllersville, PA", "Dallas, PA", "Cresson, PA", "Allentown, PA", "Ashton, PA", "Williamsport, PA", "University Park, PA", "Abington, PA", "Altoola, PA", "Monaca, PA", "Media, PA", "DuBois, PA", "Lemont Furnace, PA", "McKeesport, PA", "Middletown, PA", "Hazleton, PA", "Center Valley, PA", "Mont Alto, PA", "New Kensington, PA", "Schuylkill Haven, PA", "Dunmore, PA", "Sharon, PA", "Lehman, PA", "York, PA", "Oakdale, PA", "Moon Township, PA", "Rosemount, PA", "Wynnewood, PA", "Loretto, PA", "Latrobe, PA", "Greensburg, PA", "Shippensburg, PA", "Slippery Rock, PA", "Trevose, PA", "Selinsgrove, PA", "Swarthmore, PA", "Greenville, PA", "Bradford, PA", "Johnstown, PA", "Phoenixville, PA", "Collegeville, PA", "Villanova, PA", "Washington, PA", "Waynesburg, PA", "West Chester, PA", "New Wilmington, PA", "Chester, PA", "Wilkes-Barre, PA", "Chambersburg, PA", "California, PA", "Pittsburgh, PA", "Allentown, PA", "Summerdale, PA", "Philadelphia, PA", "Cheyney, PA", "Clarion, PA", "South Abington Township, PA", "Doylestown, PA", "Center Valley, PA", "Fort Washington, PA", "Ft. Washington, PA", "Carlisle, PA", "East Stroudsburg, PA", "Saint Davids, PA", "St. Davids, PA", "Edinboro, PA", "Elizabethtown, PA", "Lancaster, PA", "Erie, PA", "Beaver Falls, PA", "Gettysburg, PA", "Melrose Park, PA", "Grove City, PA", "Gwynedd Valley, PA", "Harrisburg, PA", "Haverford, PA", "Immaculata, PA", "Indiana, PA", "Huntingdon, PA", "La Plume, PA", "Wilkes Barre, PA", "Kutztown, PA", "Scranton, PA", "Easton, PA", "Annville, PA", "Bethlehem, PA", "Lincoln University, PA", "Lock Haven, PA", "Williamsport, PA", "Jenkintown, PA", "Mansfield, PA", "Mechanicsburg, PA", "MIllersville, PA", "Dallas, PA", "Cresson, PA", "Allentown, PA", "Ashton, PA", "University Park, PA", "Abington, PA", "Altoola, PA", "Monaca, PA", "Media, PA", "DuBois, PA", "Lemont Furnace, PA", "McKeesport, PA", "Middletown, PA", "Hazleton, PA", "Center Valley, PA", "Mont Alto, PA", "New Kensington, PA", "Schuylkill Haven, PA", "Dunmore, PA", "Sharon, PA", "Lehman, PA", "Oakdale, PA", "Moon Township, PA", "Rosemount, PA", "Wynnewood, PA", "Loretto, PA", "Latrobe, PA", "Greensburg, PA", "Shippensburg, PA", "Slippery Rock, PA", "Trevose, PA", "Selinsgrove, PA", "Swarthmore, PA", "Greenville, PA", "Bradford, PA", "Johnstown, PA", "Phoenixville, PA", "Collegeville, PA", "Villanova, PA", "Washington, PA", "Waynesburg, PA", "West Chester, PA", "New Wilmington, PA", "Chester, PA", "Wilkes-Barre, PA", "Chambersburg, PA",
                  
                  "Providence, RI", "Smithfield, RI", "East Greenwich, RI", "Bristol, RI", "Newport, RI", "Kingston, RI",
                  
                  "Columbia, SC", "Charleston, SC", "Anderson, SC", "Greenville, SC", "Orangeburg, SC", "Clemson, SC", "Rock Hill, SC", "Conway, SC", "Hartsville, SC", "Spartanburg, SC", "Due West, SC", "Florence, SC", "Greenwood, SC", "Gaffney, SC", "Sumter, SC", "Newberry, SC", "Tigerville, SC", "Clinton, SC", "Central, SC", "Aiken, SC", "Bluffton, SC", "Denmark, SC",
                  
                  "Sioux Falls, SD", "Spearfish, SD", "Madison, SD", "Mitchell, SD", "Yankton, SD", "Ellsworth Air Force Base, SD", "Rapid City, SD", "Aberdeen, SD", "Kyle, SD", "Mission, SD", "Brookings, SD", "Vermillion, SD",
                  
                  "Nashville, TN", "Clarksville, TN", "Memphis, TN", "McKenzie, TN", "Dayton, TN", "Jefferson City, TN", "Lebanon, TN", "Johnson City, TN", "Henderson, TN", "Knoxville, TN", "Clarkesville, TN", "Murfreesboro, TN", "Bristol, TN", "Jackson, TN", "Cleveland, TN", "Harrogate, TN", "Pulaski, TN", "Maryville, TN", "Milligan, TN", "Collegedale, TN", "Cookeville, TN", "Athens, TN", "Chattanooga, TN", "Martin, TN", "Sewanee, TN", "Greeneville, TN", "Cordova, TN", "Gallatin, TN", "Franklin, TN",
                  
                  "Abilene, TX", "Garland, TX", "Houston, TX", "San Angelo, TX", "Dallas, TX", "Arlington, TX", "Sherman, TX", "Austin, TX", "San Antonio, TX",  "Jacksonville, TX", "Waco, TX", "Lake Jackson, TX", "McKinney, TX", "Richardson, TX", "Irving, TX", "Marshall, TX", "Galveston, TX", "Cedar Park, TX", "Conroe, TX", "Denison, TX", "Brownwood, TX", "Hawkins, TX", "Beaumont, TX", "Laredo, TX", "Longview, TX", "Lubbock, TX", "Bedford, TX", "Midland, TX", "Wichita Falls, TX", "Georgetown, TX", "Killeen, TX", "Mesquite, TX", "Stafford, TX", "Prairie View, TX", "Fort Worth , TX", "Huntsville, TX", "Kerrville, TX", "McAllen, TX", "Round Rock, TX", "El Paso, TX", "Keene, TX", "Waxahachie, TX", "Terrell, TX", "Nacogdoches, TX", "Alpine, TX", "Stephenville, TX", "College Station, TX", "Commerce, TX", "Corpus Christi, TX", "Kingsville, TX", "Texarkana, TX", "Tyler, TX", "Seguin, TX", "San Marcos, TX", "Denton, TX", "Southlake, TX", "Odessa, TX", "Edinburg, TX", "Victoria, TX", "Belton, TX", "Plainview, TX", "Canyon, TX",
                  
                  "Draper, UT", "Provo, UT", "West Jordan, UT", "Orem, UT", "Saint George, UT", "St. George, UT", "Layton, UT", "Murray, UT", "Salt Lake City, UT", "Ephraim, UT", "Cedar City, UT", "West Haven, UT", "Logan, UT", "Ogden, UT",
                  
                  "Bennington, VT", "Castleton, VT", "Burlington, VT", "Plainfield, VT", "Putney, VT", "Marlboro, VT", "Middlebury, VT", "Montpelier, VT", "Johnson, VT", "Northfield, VT", "Colchester, VT", "Craftsbury Common, VT", "Randolph, VT",
                  
                  "Salem, VA", "Danville, VA", "Hampton, VA", "Bluefield, VA", "Richmond, VA", "Bridgewater, VA", "Virginia Beach, VA", "Lynchburg, VA", "Chesapeake, VA", "Arlington, VA", "Newport News, VA", "Harrisonburg, VA", "Emory, VA", "Fairfax, VA", "Ferrum, VA", "Hampden-Sydney, VA", "Hampden Sydney, VA", "Hampton, VA", "Roanoke, VA", "Vienna, VA", "Farmville, VA", "Staunton, VA", "Norfolk, VA", "Purcellville, VA", "Radford, VA", "Ashland, VA", "Winchester, VA", "Glen Allen, VA", "Buena Vista, VA", "Sweet Briar, VA", "Wise, VA", "Fredericksburg, VA", "University of Richmond, VA", "Falls Church, VA", "Lexington, VA", "Blacksburg, VA", "Petersburg, VA", "Williamsburg, VA",
                  
                  "Seattle, WA", "Kenmore, WA", "Bellevue, WA", "Bellingham, WA", "Bothell, WA", "Ellensburg, WA", "Centralia, WA", "Vancouver, WA", "Lakewood, WA", "Pasco, WA", "Redmond, WA", "Cheney, WA", "Lynnwood, WA", "Tacoma, WA", "Spokane, WA", "Aberdeen, WA", "Auburn, WA", "Toppenish, WA", "Des Moines, WA", "Kirkland, WA", "Longview, WA", "Bremerton, WA", "Port Angeles, WA", "Renton, WA", "Lacey, WA", "Mount Vernon, WA", "Olympia, WA", "Tukwila, WA", "Walla Walla, WA", "College Place, WA", "Pullman, WA", "Wenatchee, WA", "Yakima, WA",
                  
                  "Philippi, WV", "Charles Town, WV", "Mount Hope, WV", "Bethany, WV", "Bluefield, WV", "Athens, WV", "Elkin, WV", "Fairmont, WV", "Glenville, WV", "Huntington, WV", "Vienna, WV", "Keyser, WV", "Salem, WV", "Shepherdstown, WV", "Scott Depot, WV", "Charleston, WV", "Martinsburg, WV", "West Liberty, WV", "Institute, WV", "Morgantown, WV", "Parkersburg, WV", "Beckley, WV", "Buckhannon, WV", "Wheeling, WV",
                  
                  "Milwaukee, WI", "Green Bay, WI", "Beloit, WI", "Wauwatosa, WI", "Waukesha, WI", "Kenosha, WI", "Keshena, WI", "Glendale, WI", "Mequon, WI", "Madison, WI", "Brookfield, WI", "Manitowoc, WI", "Plymouth, WI", "Appleton, WI", "Watertown, WI", "Fond du Lac, WI", "Ashland, WI", "Ripon, WI", "De Pere, WI", "Eau Claire, WI", "La Crosse, WI", "Oshkosh, WI", "Platteville, WI", "River Falls, WI", "Stevens Point, WI", "Menomonie, WI", "Superior, WI", "Whitewater, WI",
                  
                  "Laramie, WY",
                  
                  "Normal, AL", "Montgomery, AL", "Athens, AL", "Auburn, AL", "Birmingham, AL", "Orange Beach, AL", "Florence, AL", "Huntsville, AL", "Jacksonville, AL", "Marion, AL", "Fairfield, AL", "Mobile, AL", "Selma, AL", "Tuscaloosa, AL", "Talladega, AL", "Troy, AL", "Tuskegee, AL", "Daphne, AL", "Montevallo, AL", "Livingston, AL",
                  
                  "Palmer, AK", "Anchorage, AK", "Barrow, AK", "Fairbanks, AK", "Juneau, AK",
                  
                  "Chandler, AZ", "Phoenix, AZ", "Glendale, AZ", "Tempe, AZ", "Mesa, AZ", "Scottsdale, AZ", "Tucson, AZ", "Tsaile, AZ", "Prescott, AZ", "Flagstaff, AZ", "Surprise, AZ", "Sierra Vista, AZ",
                  
                  "Little Rock, AR", "Jonesboro, AR", "Russellville, AR", "Conway, AR", "Hot Springs, AR", "Paragould, AR", "Springdale, AR", "Searcy, AR", "Arkadelphia, AR", "Siloam Springs, AR", "Batesville, AR", "Magnolia, AR", "Fayetteville, AR", "Monticello, AR", "Pine Bluff, AR", "Fort Smith, AR", "Clarkesville, AR", "Walnut Ridge, AR",
                  
                  "Glendale, CA", "San Francisco, CA", "San Diego, CA", "Los Angeles, CA", "Signal Hill, CA", "Lancaster, CA", "Santa Barbara, CA", "Pasadena, CA", "Whitter, CA", "Azusa , CA", "Bakersfield, CA", "Penngrove, CA", "Anaheim, CA", "Beverly Hills, CA", "La Mirada, CA", "Irvine, CA", "Riverside, CA", "Fresno, CA", "Garden Grove, CA", "Valencia, CA", "Berkeley, CA", "Thousand Oaks, CA", "San Luis Obispo, CA", "Pomona, CA", "Vallejo, CA", "Long Beach, CA", "Camarillo, CA", "Chico, CA", "Carson, CA", "Hayward, CA", "Fullerton, CA", "Seaside, CA", "Northridge, CA", "Sacramento, CA", "San Bernardino, CA", "San Marcos, CA", "Turlock, CA", "Santa Ana, CA", "Rancho Cordova, CA", "Orange, CA", "Claremont, CA", "San Jose, CA", "Tarzana, CA", "Cypress, CA", "Ontario, CA", "San Rafael, CA", "Quincy, CA", "Los Altos Hills, CA", "Cerritos, CA", "Hollywood, CA", "San Mateo, CA", "Oakland, CA", "Torrance, CA", "Roseville, CA", "Arcata, CA", "Stockton, CA", "Newport Beach, CA", "Pleasant Hill, CA", "Escondido, CA", "Laguna Beach, CA", "San Dimas, CA", "Loma Linda, CA", "Van Nuys, CA", "Rancho Palos Verdes, CA", "Santa Fe Springs, CA", "Atherton, CA", "Monterey, CA", "Oceanside, CA", "Modesto, CA", "La Jolla, CA", "Burbank, CA", "Fremont, CA", "Belmont, CA", "Costa Mesa, CA", "Angwin, CA", "Palo Alto, CA", "Malibu, CA", "Alhambra, CA", "Whittier, CA", "Emeryville, CA", "Moraga, CA", "Santee, CA", "Visalia, CA", "Santa Clara, CA", "Santa Monica, CA", "Redding, CA", "San Bruno, CA", "Aliso Viejo, CA", "Rohnert Park, CA", "El Cajon, CA", "Stanford, CA", "El Dorado Hills, CA", "Santa Clarita, CA", "Temecula, CA", "Santa Paula, CA", "Los Alamitos, CA", "Davis, CA", "Merced, CA", "Santa Cruz, CA", "La Verne, CA", "Redlands, CA", "Rosemead, CA", "Inglewood, CA", "North Hollywood, CA", "Culver City, CA", "Rocklin, CA",
                  
                  "Alamosa, CO", "Aurora, CO", "Littleton, CO", "Denver, CO", "Colorado Springs, CO", "Fort Collins, CO", "Lakewood, CO", "Grand Junction, CO", "Glenwood Springs, CO", "Golden, CO", "Pueblo, CO", "Westminster, CO", "Durango, CO", "Fort Morgan, CO", "Boulder, CO", "Centennial, CO", "USAF Academy, CO", "Greeley, CO", "Lone Tree, CO", "Gunnison, CO", "United States Air Force Academy, CO",
                  
                  "New Haven, CT", "New Britain, CT", "New London, CT", "Willimantic, CT", "Fairfield, CT", "East Hartford, CT", "Cromwell, CT", "Hamden, CT", "Waterbury, CT", "Hamden, CT", "Hartford, CT", "Bridgeport, CT", "Storrs, CT", "Groton, CT", "Stamford, CT", "West Hartford, CT", "West Haven, CT", "Middletown, CT", "Danbury, CT",
                  
                  "Dover, DE", "Wilmington, DE", "Newark, DE", "New Castle, DE",
                  
                  "Miami, FL", "Orlando, FL", "Fort Lauderdale, FL", "Ave Maria, FL", "Leesburg, FL", "Daytona Beach, FL", "Delray Beach, FL", "Altamonte Springs, FL", "Jacksonville, FL", "Marianna, FL", "Gainesville, FL", "Ocala, FL", "Ormond Beach, FL", "Miramar, FL", "Cocoa, FL", "Saint Petersburg, FL", "St. Petersburg, FL", "Boca Raton, FL", "Tampa, FL", "St. Augustine, FL", "Saint Augustine, FL", "Tallahassee, FL", "Temple Terrace, FL", "Lake City, FL", "Fort Myers, FL", "Melbourne, FL", "Hialeah, FL", "Lakeland, FL", "Winter Park, FL", "Panama City, FL", "West Palm Beach, FL", "Hobe Sound, FL", "Naples, FL", "Fort Pierce, FL", "North Miami, FL", "Kissimmee, FL", "Pembroke Pines, FL", "Miami Springs, FL", "Doral, FL", "Sarasota, FL", "Madison, FL", "Niceville, FL", "Lake Worth, FL", "New Port Richey, FL", "Pensacola, FL", "Winter Haven, FL", "Ocala, FL", "Lake Mary, FL", "Palatka, FL", "Saint Leo, FL", "St. Leo, FL", "Largo, FL", "Sanford, FL", "Deerfield Beach, FL", "Avon Park, FL", "Royal Palm Beach, FL", "Clearwater, FL", "Miami Gardens, FL", "Bradenton, FL", "DeLand, FL", "Graceville, FL", "Key West, FL", "Trinity, FL", "Lauderhill, FL", "Coral Gables, FL", "Lake Wales, FL", "Babson Park, FL",
                  
                  "Tifton, GA", "Decatur, GA", "Albany, GA", "Cuthbert, GA", "Atlanta, GA", "Augusta, GA", "Mount Berry, GA", "Gainesville, GA", "Mount Vernon, GA", "Morrow, GA", "Brunswick, GA", "Columbus, GA", "Lookout Mountain, GA", "Dalton, GA", "Swainsboro, GA", "Franklin Springs, GA", "Fort Valley, GA", "Milledgeville, GA", "Lawrenceville, GA", "Rome, GA", "Statesboro, GA", "Americus, GA", "Barnesville, GA", "Kennesaw, GA", "Lagrange, GA", "Marietta, GA", "Lithonia, GA", "Macon, GA", "Kings Bay, GA", "Demorest, GA", "West Point, GA", "Waleska, GA", "Savannah, GA", "Douglas, GA", "Thomasville, GA", "Toccoa Falls, GA", "Cleveland , GA", "Athens, GA", "Dahlonega, GA", "Carrollton, GA", "Valdosta, GA", "Young Harris, GA",
                  
                  "Laie, HI", "Honolulu, HI", "Hilo, HI", "Kahului, HI", "Kapolei, HI",
                  
                  "Boise, ID", "Rexburg, ID", "Twin Falls, ID", "Pocatello, ID", "Lewiston, ID", "Moscow, ID", "Nampa, ID", "Idaho Falls, ID", "Caldwell, ID",
                  
                  "Hoffman Estates, IL", "Chicago, IL", "Rock Island, IL", "Aurora, IL", "Lisle, IL", "Carlinville, IL", "Quincy, IL", "Peoria, IL", "Downers Grove, IL", "Addison, IL", "Mount Prospect, IL", "River Forest, IL", "Naperville, IL", "Charleston, IL", "Elmhurst, IL", "Eureka, IL", "University Park, IL", "Greenville, IL", "Skokie, IL", "Jacksonville, IL", "Normal, IL", "Bloomington, IL", "Elgin, IL", "Galesburg, IL", "Danville, IL", "Romeoville, IL", "Lincoln, IL", "Lebanon, IL", "Monmouth, IL", "Lombard, IL", "Dekalb, IL", "Bridgeview, IL", "Evanston, IL", "Bourbannais, IL", "Elsah, IL", "Rockford, IL", "Carbondale, IL", "Edwardsville, IL", "Springfield, IL", "Palos Heights, IL", "Deerfield, IL", "Champaign, IL", "Urbana, IL", "Joliet, IL", "Macomb, IL", "Wheaton, IL",
                  
                  "Indianapolis, IN", "Anderson, IN", "Crawfordsville, IN", "Muncie, IN", "Mishawaka, IN", "Whiting, IN", "Greencastle, IN", "Merrillville, IN", "Goshen, IN", "Richmond, IN", "Franklin, IN", "Winona Lake, IN", "Hanover, IN", "Notre Dame, IN", "Huntington, IN", "Fort Wayne, IN", "Terre Haute, IN", "Bloomington, IN", "Kokomo, IN", "Gary, IN", "South Bend, IN", "New Albany, IN", "Marion, IN", "North Manchester, IN", "Jeffersonville, IN", "Oakland City, IN", "Hammond, IN", "West Lafayette, IN", "Saint Mary of the Woods, IN", "St. Mary of the Woods, IN", "Upland, IN", "Angola, IN", "Westfield, IN", "Evansville, IN", "Valparaiso, IN", "Greendale, IN", "Vincennes, IN",
                  
                  "Waterloo, IA", "Sioux City, IA", "Storm Lake, IA", "Pella, IA", "Dubuque, IA", "Cedar Rapids, IA", "Mount Vernon, IA", "Epworth, IA", "Sioux Center, IA", "Des Moines, IA", "Ankeny, IA", "Lamoni, IA", "Grinnell, IA", "Davenport, IA", "Ames, IA", "Mount Pleasant, IA", "Decorah, IA", "Fairfield, IA", "Orange City, IA", "Kalona, IA", "Indianola, IA", "Iowa City, IA", "Fayette, IA", "Forest City, IA", "Oskaloosa, IA", "Waverly, IA",
                  
                  "Baldwin City, KS", "Haviland, KS", "Atchison, KS", "Lindsborg, KS", "North Newton, KS", "McPherson, KS", "Overland Park, KS", "Kansas City, KS", "Emporia, KS", "Hays, KS", "Wichita, KS", "Lenexa, KS", "Lawrence, KS", "Hesston, KS", "Manhattan, KS", "Salina, KS", "Olathe, KS", "Garden City, KS", "Ottawa, KS", "Pittsburg, KS", "Topeka, KS", "Winfield, KS", "Sterling, KS", "Hillsboro, KS", "Leavenworth, KS",
                  
                  "Pippa Passes, KY", "Lexington, KY", "Wilmore, KY", "Florence, KY", "Louisville, KY", "Berea, KY", "Owensboro, KY", "Campbellsville, KY", "Danville, KY", "Pineville, KY", "Richmond, KY", "Georgetown, KY", "Bowling Green, KY", "Grayson, KY", "Jackson, KY", "Frankfort, KY", "Owensboro, KY", "Columbia, KY", "Midway, KY", "Moorehead, KY", "Murray, KY", "Highland Heights, KY", "Crestview Hills, KY", "Lexington, KY", "Barbourville, KY", "Pikeville, KY", "Williamsburg, KY",
                  
                  "Shreveport, LA", "Jefferson, LA", "New Orleans, LA", "Baton Rouge, LA", "Grambling, LA", "Kenner, LA", "Pineville, LA", "Ruston, LA", "Lake Charles, LA", "Thibodaux, LA", "Natchitoches, LA", "St. Benedict, LA", "Saint Benedict, LA", "Hammond, LA", "Lafayette, LA", "Monroe, LA",
                  
                  "Lewiston, ME", "Bangor, ME", "Brunswick, ME", "Waterville, ME", "Bar Harbor, ME", "Portland, ME", "Castine, ME", "Standish, ME", "Unity, ME", "Orono, ME", "Augusta, ME", "Farmington, ME", "Fort Kent, ME", "Machias, ME", "Presque Isle, ME", "Biddleford, ME",
                  
                  "Baltimore, MD", "Bowie, MD", "Laurel, MD", "Frostburg, MD", "Frederick, MD", "Capitol Heights, MD", "Westminster, MD", "Emmitsburg, MD", "Salisbury, MD", "Annapolis, MD", "St. Mary’s City, MD", "Saint Mary’s City, MD", "Stevenson, MD", "Suitland, MD", "Townson, MD", "Princess Anne, MD", "Adelphi, MD", "College Park, MD", "Takoma Park, MD", "Chestertown, MD", "Silver Spring, MD",
                  
                  "Cambridge, MA", "Boston, MA", "Springfield, MA", "Amherst, MA", "Paxton, MA", "Worcester, MA", "Wellesley, MA", "Great Barrington, MA", "Longmeadow, MA", "Waltham, MA", "Chestnut Hill, MA", "Bridgewater, MA", "Chicopee, MA", "Milton, MA", "Franklin, MA", "Quincy, MA", "Beverly, MA", "Fitchburg, MA", "Framingham, MA", "Needham, MA", "Wenham, MA", "Brookline, MA", "Newton Centre, MA", "Newton, MA", "North Adams, MA", "Buzzards Bay, MA", "North Andover, MA", "South Hadley, MA", "Dudley, MA", "Haverhill, MA", "Weston, MA", "Brighton, MA", "Salem, MA", "Northampton, MA", "Easton, MA", "Medford, MA", "North Dartmouth, MA", "Lowell, MA", "Norton, MA", "Williamstown, MA",
                  
                  "Adrian, MI", "Albion, MI", "Alma, MI", "Alpena, MI", "Berrien Springs, MI", "Grand Rapids, MI", "Owosso, MI", "Brimley, MI", "Mount Pleasant, MI", "Troy, MI", "Howell, MI", "Detroit, MI", "Ann Arbor, MI", "Ypsilanti, MI", "Big Rapids, MI", "Hancock, MI", "Wyoming, MI", "Allendale, MI", "Lansing, MI", "Dearborn, MI", "Hillsdale, MI", "Holland, MI", "Jackson, MI", "Kalamazoo, MI", "Flint, MI", "Benton Harbor, MI", "Sault Ste Marie, MI", "Southfield, MI", "Livonia, MI", "East Lansing, MI", "Houghton, MI", "Marquette, MI", "Traverse City, MI", "Midland, MI", "Rochester Hills, MI", "Olivet, MI", "University Center, MI", "Novi, MI", "Spring Arbor, MI", "Southfield, MI", "Oak Park, MI",
                  
                  
                  "Chicago, IL--IN", "Washington, DC--VA--MD", "New York--Newark, NY--NJ--CT", "Cincinnati, OH--KY--IN", "Las Vegas--Henderson, NV", "Kansas City, MO--KS", "Los Angeles--Long Beach--Anaheim, CA", "Charleston--North Charleston, SC", "Springfield, MA--CT", "Charles Town--Ranson, WV", "Richmond, IN--OH", 
                  "St. Louis, MO--IL", "Fayetteville--Springdale--Rogers, AR--MO", "Conroe--The Woodlands, TX", "Murrieta--Temecula--Menifee, CA", "Minneapolis--St. Paul, MN--WI", "Denver--Aurora, CO", "Palm Coast--Daytona Beach--Port Orange, FL", "Charlotte, NC--SC", "San Francisco--Oakland, CA", 
                  "Ogden--Layton, UT", "Louisville/Jefferson County, KY--IN", "Memphis, TN--MS--AR", "Tampa--St. Petersburg, FL", "Chattanooga, TN--GA", "Portland, OR--WA", "Bridgeport--Stamford, CT--NY", "Philadelphia, PA--NJ--DE--MD", "Dallas--Fort Worth--Arlington, TX", "Bloomsburg--Berwick, PA", "Toledo, OH--MI", "Allentown, PA--NJ", 
                  "Worcester, MA--CT", "Grand Forks, ND--MN", "Phoenix--Mesa, AZ", "Boston, MA--NH--RI", "Norwich--New London, CT--RI", "El Paso, TX--NM", "Omaha, NE--IA", "South Bend, IN--MI", "Pensacola, FL--AL", "Riverside--San Bernardino, CA", "Providence, RI--MA", "Poughkeepsie--Newburgh, NY--NJ", "Albany--Schenectady, NY", "Huntington, WV--KY--OH", 
                  "Sarasota--Bradenton, FL", "Columbus, GA--AL", "Fargo, ND--MN", "Kenosha, WI--IL", "Kennewick--Pasco, WA", "Youngstown, OH--PA", "Olympia--Lacey, WA", "Reno, NV--CA", "Sioux City, IA--NE--SD", "College Station--Bryan, TX", "Denton--Lewisville, TX", "Weirton--Steubenville, WV--OH--PA", "Salt Lake City--West Valley City, UT", "Fort Smith, AR--OK", "Walla Walla, WA--OR",
                  "Monessen--California, PA", "Staunton--Waynesboro, VA", "Westminster--Eldersburg, MD", "Lancaster--Palmdale, CA", "Portsmouth, OH--KY", "Salisbury, MD--DE", "Danbury, CT--NY", "East Liverpool, OH--WV--PA", 
                  "Marietta, OH--WV", "Lorain--Elyria, OH", "Bloomington--Normal, IL", "Clarksville, TN--KY", "St. Joseph, MO--KS", "New Philadelphia--Dover, OH", "Nashua, NH--MA", "Seaside--Monterey, CA", "Prescott Valley--Prescott, AZ", "Davenport, IA--IL", "Benton Harbor--St. Joseph--Fair Plain, MI", 
                  "Milton--Lewisburg, PA", "Bristol--Bristol, TN--VA", "Provo--Orem, UT", "South Lyon--Howell, MI", "Palm Bay--Melbourne, FL", "Danville, VA--NC", "Wheeling, WV--OH", "Bluefield, WV--VA", "Atchison, KS--MO", "Marinette--Menominee, WI--MI", "Lewiston, ID--WA",
                  "East Stroudsburg, PA--NJ", "Evansville, IN--KY", "Longview, WA--OR", "Duluth, MN--WI", "Klamath Falls--Altamont, OR", "La Crosse, WI--MN", "Leominster--Fitchburg, MA", "Keyser, WV--MD", "Siloam Springs, AR--OK", "Leesburg--Eustis--Tavares, FL", "Emmitsburg, MD--PA", "Beloit, WI--IL", 
                  "Dubuque, IA--IL", "Arcata--McKinleyville, CA", "Wendell--Zebulon, NC", "Parkersburg, WV--OH", "Lake Jackson--Angleton, TX", "Lebanon--Hanover, NH--VT", "Sebring--Avon Park, FL", "Barre--Montpelier, VT", "Bradford, PA--NY", "Texarkana--Texarkana, TX--AR", 
                  "Daphne--Fairhope, AL", "Monmouth--Independence, OR", "Laie--Hauula, HI", "North Adams, MA--VT", "Dunkirk--Fredonia, NY", "Norton--Wise, VA", "Alma--St. Louis, MI", "Lawrenceburg--Greendale--Aurora, IN", "Incline Village, NV--CA", "Shepherdstown, WV--MD"

                  )

```

## Raw Data

```{r, echo = FALSE}
data <- data |>
  mutate(
        college_town = if_else(UA_NAME %in% college_towns, 1, 0))

data

```


```{r, include = FALSE}
data_not_college_town <- data |>
  filter(college_town == 0)

non_college_towns <- as.tibble(unique(data_not_college_town$UA_NAME))

non_college_towns

```
```{r, echo = FALSE, include = FALSE}
coffee_data <- data |>
  filter(RestaurantName %in% c("Dunkin", "Starbucks")) 

coffee_data_stats <- coffee_data |>
  group_by(RestaurantName, college_town) |>
  summarize(count = n()) |>
  pivot_wider(names_from = college_town, values_from = count) |>
  mutate(ate = `1` - `0`,
         prop_college = `1`/(`1`+`0`))

```
## First Data Visualization

```{r, echo = FALSE}
coffee_data |>
  mutate(college_town_new = if_else(college_town == 1, "College Town", "Non-College Town"),
         `Restaurant Name` = if_else(RestaurantName == "Dunkin", "Dunkin' Donuts", "Starbucks")) |>
  ggplot(mapping = aes(x = college_town_new, fill = `Restaurant Name`)) +
  geom_bar(position = "dodge") +
  labs(title = "Chain Coffee Locations and College Towns", y = "Count of Locations", x = "")


```



