---
title: "Gov 50 Final Project"
author: Alex Heuss
description: "An Analysis of Chain Coffee Locations Throughout the United States"
output:
  distill::distill_article:
    self_contained: false
---


```{r, include = FALSE}
library(tidyverse)
library(ggplot2)


```



## Introduction

Coming to Cambridge this fall, I had lots of things on my mind. Class choices, new roommates, new friends, and (perhaps more importantly) coffee. As I learned soon after arriving, coffee is not hard to find in Cambridge. This project is an effort to explore where coffee locations are located in the United States and why. After exploring my data with more depth, I realized that it would be ineffective and misleading to attempt to analyze all coffee shops based on the provided data. As a result, this project focuses on the chain coffee franchises Dunkin' Donuts and Starbucks. My primary research question was inspired by the sheer prevalence of coffee in Cambridge and asks: is there a correlation between these chain coffee locations and whether or not the city it is located in is a college town?

## The Data

My original data was taken from Friendly Cities on GitHub and includes 800,000 restaurants throughout the United States. The dataset included the variables: RestaurantName, Cuisine, OpenHours, State, CNTY_GEOID, UA_NAME, MSA_NAME, MSA_GEOID, Lon, Lat, Frequency, and isChain. This dataset was originally used to find correlation between chain restaurants and a number of independent variables, so this project goes in another direction. The primary variables I focused on included RestaurantName, which provided the name of the restaurant, UA_NAME, which is short for Urban Area name and was typically formatted as the city and state where the restaurant was located, lastly the State variable, which provided the state abbreviation for the state the restaurant was located in. As the dataset originally stood, I did not have enough data to explore my research question. I created a new tibble labeled college_towns which includes the name of every town in the United States that has a four-year higher education institution located within it. This tibble was compiled using information provided on Campus Explorer and then used to create the variable college_town within the dataset. The final two variables I added to the dataset were based on location and are called region and division. These variables were created in reference to the regions and divisions assigned to states by the United States Census Bureau. 

The dependent variable in my study is whether or not a town has a chain coffee location, in this study refering to a Dunkin' Donuts or a Starbucks. 

```{r}
part_1 <- read_csv("https://raw.githubusercontent.com/friendlycities-gatech/chainness/main/data/chainness_point_2021_part1.csv")


part_2 <- read_csv("https://raw.githubusercontent.com/friendlycities-gatech/chainness/main/data/chainness_point_2021_part2.csv")

part_3 <- read_csv("https://raw.githubusercontent.com/friendlycities-gatech/chainness/main/data/chainness_point_2021_part3.csv")

```

```{r}
data <- 
  rbind(part_1, part_2, part_3)

```


## Project Proposal

What is the relationship between chain coffee restaurants and college towns? In my project, I hope to explore the location of chain coffee locations across the United States, specifically in relation to college towns. I hypothesize there will be a higher frequency of coffee chains overall in college towns, a positive relationship. My variables of interest are restaurant name, state, county, and city, but my specific explanatory variable will be one that I create called "college_town", which will be marked with a 1 if the town has a four year higher education institution and a 0 if not.  My outcome variable of interest is frequency, as well as mean chain coffee stores in college towns, both measured as a number. My hypotheses would be supported if the frequency of chain coffee stores is higher in college towns than the frequency of chain coffee stores in non-college towns. My hypothesis would not be supported if I were to find a negative or no correlation between chain coffee stores and college towns. My project is based on a database provided by Friendly Cities on GitHub and includes 800,000 restaurants throughout the United States. The "college_town" variable is being created using information found on Campus Explorer. 


```{r}
college_towns <- c("Bloomington, MN", "Minneapolis, MN", "Bemidji, MN",  "Mankato, MN", "St. Paul, MN", "Northfield, MN", "St. Joseph, MN", "Saint Joseph, MN", "Moorhead, MN", "Saint Bonifacius, MN", "St. Bonifacous, MN", "St. Peter, MN", "Saint Peter, MN", "St. Louis Park, MN", "Saint Louis Park, MN", "New Ulm, MN", "St. Cloud, MN", "Saint Cloud, MN", "Collegeville, MN", "Winona, MN", "Marshall, MN", "Duluth, MN", "Crookston, MN", "Morris, MN", "Rochester, MN",
  
                   "Alcorn State, MS", "Jackson, MS", "Blue Mountain, MS"," Cleveland, MS", "Clinton, MS", "Mississippi State, MS", "Columbus, MS", "Itta Bena, MS", "Holly Springs, MS", "Laurel, MS", "Tougaloo, MS", "University, MS", "Hattiesburg, MS",
                   
                   "St. Joseph, MO", "Kansas City, MO", "Springfield, MO", "Moberly, MO", "Fayette, MO", "Point Lookout, MO", "Columbia, MO", "Conception, MO", "Nevada, MO"," Canton, MO", "Hannibal, MO", "Jefferson City, MO", "St. Charles, MO", "Chesterfield, MO", "Joplin, MO", "Rolla, MO", "Marshall, MO", "St. Joseph, MO", "Maryville, MO", "Parkville, MO", "Florissant, MO", "Cape Girardeau, MO", "Bolivar, MO", "Fenton, MO", "Kirksville, MO", "Warrensburg, MO", "Wentzville, MO", "Fulton, MO", "Liberty, MO",
                   
                  "Helena, MT", "Bozeman, MT", "Billings, MT", "Havre, MT", "Butte, MT", "Pablo, MT", "Missoula, MT", "Box Elder, MT", "Dillon, MT", "Great Falls, MT",
                  
                  "Bellevue, NE", "Lincoln, NE", "Chadron, NE", "Omaha, NE", "Seward, NE", "Hastings, NE", "Crete, NE", "Fremont, NE", "Papillion, NE", "Peru, NE", "Gering, NE", "Kearney, NE", "Wayne, NE", "York, NE",
                  
                  "Las Vegas, NV", "Henderson, NV", "Elko, NV", "Reno, NV", "Incline Village, NV", "Carson City, NV",
                  
                  "New London, NH", "Hanover, NH", "Rindge, NH", "Concord, NH", "Keene, NH", "Warner, NH", "Henniker, NH", "Plymouth, NH", "Nashua, NH", "Manchester, NH", "Merrimack, NH", "Durham, NH",
                  
                  "Lakewood, NJ", "Woodland Park, NJ", "Bloomfield, NJ", "Caldwell, NJ", "Hackettstown, NJ", "North Brunswick, NJ", "Morristown, NJ", "Madison, NJ", "Belleville, NJ", "Jersey City, NJ", "Ramsey, NJ", "Teaneck, NJ", "Lodi, NJ", "Union, NJ", "West Long Branch, NJ", "Montclair, NJ", "Newark, NJ", "Princeton, NJ", "Edison, NJ", "Mahwah, NJ", "Lawrenceville, NJ", "Glassboro, NJ", "Camden, NJ", "South Orange, NJ", "Hoboken, NJ", "Galloway, NJ", "Cherry Hill, NJ", "Adelphia, NJ", "Ewing, NJ", "Trenton, NJ", "Wayne, NJ", "Keyport, NJ", "North Plainfield, NJ", "Elizabeth, NJ", "Howell, NJ",
                  
                  "Albuquerque, NM", "Portales, NM", "Santa Fe, NM", "Crownpoint, NM", "Las Vegas, NM", "Socorro, NM", "Las Cruces, NM", "Espanola, NM", "Hobbs, NM", "Silver City, NM",
                  
                  "Garden City, NY", "Albany, NY", "Alfred, NY", "New York, NY", "New York City, New York", "Brooklyn, NY", "Monsey, NY", "Annandale-On-Hudson, NY", "Spring Valley, NY", "Far Rockaway, NY", "Vestal, NY", "Buffalo, NY", "Rochester, NY", "Orchard Park, NY", "Liverpool, NY", "Cazenovia, NY", "Potsdam, NY", "Hamilton, NY", "Bronx, NY", "Staten Island, NY", "Bronxville, NY", "Ithaca, NY", "Hyde Park, NY", "Queens, NY", "Jamaica, NY", "Amherst, NY", "Johnson City, NY", "Orangeburg, NY", "Elmira, NY", "Farmingdale, NY", "Dix Hills, NY", "Clinton, NY", "Oneonta, NY", "Hamburg, NY", "Geneva, NY", "Hempstead, NY", "Houghton, NY", "New Rochelle, NY", "Jamestown, NY", "Ossining, NY", "Keuka Park, NY", "Syracuse, NY", "Brookville, NY", "Riverdale, NY", "Purchase, NY", "Poughkeepsie, NY", "Dobbs Ferry, NY", "Rockville Centre, NY", "Newburgh, NY", "Syosset, NY", "Mineola, NY"," Old Westbury, NY", "Niagara University, NY", "Peekskill, NY", "Paul Smiths, NY", "Forest Hills, NY", "Long Beach, NY", "Flushing, NY", "Troy, NY", "Lawrence, NY", "Loudonville, NY", "Saratoga Springs, NY", "St. Bonaventure, NY", "Saint Bonaventure, NY", "Brooklyn Heights, NY", "Canton, NY", "Patchogue, NY", "Sparkill, NY", "New Paltz, NY", "Stony Brook, NY", "Fredonia, NY", "Brockport, NY", "Geneseo, NY", "Oswego, NY", "Plattsburgh, NY", "Potsdam, NY", "Cobleskill, NY", "Delhi, NY", "Cortland, NY", "Throggs Neck, NY", "Morrisville, NY", "Utica, NY", "White Plains, NY", "Schenectady, NY", "Kings Point, NY", "West Point, NY", "Glen Cove, NY", "Aurora, NY", "Mount Kisco, NY", "Greenfield Park, NY", "New Windsor, NY", "Kew Gardens, NY", "Suffern, NY", "Monroe, NY", "South Fallsburg, NY",
                  
                  "Durham, NC", "Boone, NC", "Wilson, NC", "Belmont, NC", "Greensboro, NC", "Brevard, NC", "Concord, NC", "Buies Creek, NC", "Winston Salem, NC", "Fayetteville, NC", "Charlotte, NC", "Salisbury, NC", "Murfreesboro, NC", "Davidson, NC", "Greenville, NC", "Elizabeth City, NC", "Elon, NC", "Boiling Springs, NC", "Dunn, NC", "High Point, NC", "Banner Elk, NC", "Raleigh, NC", "Hickory, NC", "Salisbury, NC", "Mars Hill, NC", "Montreat, NC", "Rocky Mount, NC", "Misenheimer, NC", "Winston-Salem, NC", "Wilmington, NC", "Wake Forest, NC", "Wendell, NC", "Laurinburg, NC", "Morrisville, NC", "Mount Olive, NC", "Asheville, NC", "Chapel Hill, NC", "Pembroke, NC", "Henderson, NC", "Swannanoa, NC", "Cullowhee, NC", "Wingate, NC",
                  
                  "Bismarck, ND", "Dickinson, ND", "Mayville, ND", "Minot, ND", "Fargo, ND", "New Town, ND", "Fort Yates, ND", "Ellendale, ND", "Belcourt, ND", "Jamestown, ND", "Grand Forks, ND", "Valley City, ND",
                  
                  "Salem, OH", "Yellow Springs, OH", "Cincinnati, OH", "Ashland, OH", "Canton, OH", "Berea, OH", "Bluffton, OH", "Huron, OH", "Bowling Green, OH", "Parma, OH", "Columbus, OH", "Cleveland, OH", "Cedarville, OH", "Wilberforce, OH", "Springfield, OH", "Defiance, OH", "Granville, OH", "Steubenville, OH", "Tiffin, OH", "Akron, OH", "Hiram, OH", "Westerville, OH", "University Heights, OH", "Ashtabula, OH", "East Liverpool, OH", "Burton, OH", "Kent, OH", "Warren, OH", "New Philadelphia, OH", "Gambier, OH", "Kettering, OH", "Painesville, OH", "Elyria, OH", "Sylvania, OH", "Marietta, OH", "Toledo, OH", "Hamilton, OH", "Middletown, OH", "Oxford, OH", "Mount Vernon, OH", "New Concord, OH", "Mansfield, OH", "Oberlin, OH", "Circleville, OH", "Ada, OH", "Lima, OH", "Marion, OH", "Newark, OH", "Chillicothe, OH", "Saint Clairesville, OH", "St. Clairesville, OH", "Lancaster, OH", "Athens, OH", "Ironton, OH", "Zanesville, OH", "Delaware, OH", "Wickliffe, OH", "Portsmouth, OH", "Dayton, OH", "Warrensville Heights, OH", "Wooster, OH", "Lakewood, OH", "Findlay, OH", "South Point, OH", "Blue Ash, OH", "Batavia, OH", "Dayton, OH", "Alliance, OH", "Rio Grande, OH", "Pepper Pike, OH", "North Canton, OH", "Wilmington, OH", "Celina, OH", "Youngstown, OH",
                  
                  "Muskogee, OK", "Lawton, OK", "Ada, OK", "Shawnee, OK", "Langston, OK", "Oklahoma City, OK", "Tulsa, OK", "Tahlequah, OK", "Alva, OK", "Edmond, OK", "Goodwell, OK", "Okmulgee, OK", "Stillwater, OK", "Bartlesville, OK", "Moore, OK", "Claremore, OK", "Durant, OK", "Bethany, OK", "Weatherford, OK", "Norman, OK", "Chickasha, OK",
                  
                  "Portland, OR", "Salem, OR", "La Grande, OR", "Newburg, OR", "McMinnville, OR", "Saint Benedict, OR", "St. Benedict, OR", "Eugene, OR", "Klamath Falls, OR", "Corvallis, OR", "Bend, OR", "Forest Grove, OR", "Beaverton, OR", "Ashland, OR", "Monmouth, OR",
                  
                  "Reading, PA", "Meadville, PA", "Glenside, PA", "Bloomsburg, PA", "Bryn Athyn, PA", "Bryn Mawr, PA", "Lewisburg, PA", "Radnor, PA", "Reading, PA", "Meadville, PA", "Glenside, PA", "Bloomsburg, PA", "Bryn Athyn, PA", "Bryn Mawr, PA", "Lewisburg, PA", "Radnor, PA", "Langhorne, PA", "California, PA", "Pittsburgh, PA", "Allentown, PA", "Summerdale, PA", "Philadelphia, PA", "Cheyney, PA", "Clarion, PA", "South Abington Township, PA", "Doylestown, PA", "Center Valley, PA", "Fort Washington, PA", "Ft. Washington, PA", "Carlisle, PA", "East Stroudsburg, PA", "Saint Davids, PA", "St. Davids, PA", "Edinboro, PA", "Elizabethtown, PA", "Lancaster, PA", "Erie, PA", "Beaver Falls, PA", "Gettysburg, PA", "Melrose Park, PA", "Grove City, PA", "Gwynedd Valley, PA", "Harrisburg, PA", "Haverford, PA", "Immaculata, PA", "Indiana, PA", "Huntingdon, PA", "La Plume, PA", "Wilkes Barre, PA", "Kutztown, PA", "Scranton, PA", "Easton, PA", "Annville, PA", "Bethlehem, PA", "Lincoln University, PA", "Lock Haven, PA", "Williamsport, PA", "Jenkintown, PA", "Mansfield, PA", "Mechanicsburg, PA", "MIllersville, PA", "Dallas, PA", "Cresson, PA", "Allentown, PA", "Ashton, PA", "Williamsport, PA", "University Park, PA", "Abington, PA", "Altoola, PA", "Monaca, PA", "Media, PA", "DuBois, PA", "Lemont Furnace, PA", "McKeesport, PA", "Middletown, PA", "Hazleton, PA", "Center Valley, PA", "Mont Alto, PA", "New Kensington, PA", "Schuylkill Haven, PA", "Dunmore, PA", "Sharon, PA", "Lehman, PA", "York, PA", "Oakdale, PA", "Moon Township, PA", "Rosemount, PA", "Wynnewood, PA", "Loretto, PA", "Latrobe, PA", "Greensburg, PA", "Shippensburg, PA", "Slippery Rock, PA", "Trevose, PA", "Selinsgrove, PA", "Swarthmore, PA", "Greenville, PA", "Bradford, PA", "Johnstown, PA", "Phoenixville, PA", "Collegeville, PA", "Villanova, PA", "Washington, PA", "Waynesburg, PA", "West Chester, PA", "New Wilmington, PA", "Chester, PA", "Wilkes-Barre, PA", "Chambersburg, PA", "California, PA", "Pittsburgh, PA", "Allentown, PA", "Summerdale, PA", "Philadelphia, PA", "Cheyney, PA", "Clarion, PA", "South Abington Township, PA", "Doylestown, PA", "Center Valley, PA", "Fort Washington, PA", "Ft. Washington, PA", "Carlisle, PA", "East Stroudsburg, PA", "Saint Davids, PA", "St. Davids, PA", "Edinboro, PA", "Elizabethtown, PA", "Lancaster, PA", "Erie, PA", "Beaver Falls, PA", "Gettysburg, PA", "Melrose Park, PA", "Grove City, PA", "Gwynedd Valley, PA", "Harrisburg, PA", "Haverford, PA", "Immaculata, PA", "Indiana, PA", "Huntingdon, PA", "La Plume, PA", "Wilkes Barre, PA", "Kutztown, PA", "Scranton, PA", "Easton, PA", "Annville, PA", "Bethlehem, PA", "Lincoln University, PA", "Lock Haven, PA", "Williamsport, PA", "Jenkintown, PA", "Mansfield, PA", "Mechanicsburg, PA", "MIllersville, PA", "Dallas, PA", "Cresson, PA", "Allentown, PA", "Ashton, PA", "University Park, PA", "Abington, PA", "Altoola, PA", "Monaca, PA", "Media, PA", "DuBois, PA", "Lemont Furnace, PA", "McKeesport, PA", "Middletown, PA", "Hazleton, PA", "Center Valley, PA", "Mont Alto, PA", "New Kensington, PA", "Schuylkill Haven, PA", "Dunmore, PA", "Sharon, PA", "Lehman, PA", "Oakdale, PA", "Moon Township, PA", "Rosemount, PA", "Wynnewood, PA", "Loretto, PA", "Latrobe, PA", "Greensburg, PA", "Shippensburg, PA", "Slippery Rock, PA", "Trevose, PA", "Selinsgrove, PA", "Swarthmore, PA", "Greenville, PA", "Bradford, PA", "Johnstown, PA", "Phoenixville, PA", "Collegeville, PA", "Villanova, PA", "Washington, PA", "Waynesburg, PA", "West Chester, PA", "New Wilmington, PA", "Chester, PA", "Wilkes-Barre, PA", "Chambersburg, PA",
                  
                  "Providence, RI", "Smithfield, RI", "East Greenwich, RI", "Bristol, RI", "Newport, RI", "Kingston, RI",
                  
                  "Columbia, SC", "Charleston, SC", "Anderson, SC", "Greenville, SC", "Orangeburg, SC", "Clemson, SC", "Rock Hill, SC", "Conway, SC", "Hartsville, SC", "Spartanburg, SC", "Due West, SC", "Florence, SC", "Greenwood, SC", "Gaffney, SC", "Sumter, SC", "Newberry, SC", "Tigerville, SC", "Clinton, SC", "Central, SC", "Aiken, SC", "Bluffton, SC", "Denmark, SC",
                  
                  "Sioux Falls, SD", "Spearfish, SD", "Madison, SD", "Mitchell, SD", "Yankton, SD", "Ellsworth Air Force Base, SD", "Rapid City, SD", "Aberdeen, SD", "Kyle, SD", "Mission, SD", "Brookings, SD", "Vermillion, SD",
                  
                  "Nashville, TN", "Clarksville, TN", "Memphis, TN", "McKenzie, TN", "Dayton, TN", "Jefferson City, TN", "Lebanon, TN", "Johnson City, TN", "Henderson, TN", "Knoxville, TN", "Clarkesville, TN", "Murfreesboro, TN", "Bristol, TN", "Jackson, TN", "Cleveland, TN", "Harrogate, TN", "Pulaski, TN", "Maryville, TN", "Milligan, TN", "Collegedale, TN", "Cookeville, TN", "Athens, TN", "Chattanooga, TN", "Martin, TN", "Sewanee, TN", "Greeneville, TN", "Cordova, TN", "Gallatin, TN", "Franklin, TN",
                  
                  "Abilene, TX", "Garland, TX", "Houston, TX", "San Angelo, TX", "Dallas, TX", "Arlington, TX", "Sherman, TX", "Austin, TX", "San Antonio, TX",  "Jacksonville, TX", "Waco, TX", "Lake Jackson, TX", "McKinney, TX", "Richardson, TX", "Irving, TX", "Marshall, TX", "Galveston, TX", "Cedar Park, TX", "Conroe, TX", "Denison, TX", "Brownwood, TX", "Hawkins, TX", "Beaumont, TX", "Laredo, TX", "Longview, TX", "Lubbock, TX", "Bedford, TX", "Midland, TX", "Wichita Falls, TX", "Georgetown, TX", "Killeen, TX", "Mesquite, TX", "Stafford, TX", "Prairie View, TX", "Fort Worth , TX", "Huntsville, TX", "Kerrville, TX", "McAllen, TX", "Round Rock, TX", "El Paso, TX", "Keene, TX", "Waxahachie, TX", "Terrell, TX", "Nacogdoches, TX", "Alpine, TX", "Stephenville, TX", "College Station, TX", "Commerce, TX", "Corpus Christi, TX", "Kingsville, TX", "Texarkana, TX", "Tyler, TX", "Seguin, TX", "San Marcos, TX", "Denton, TX", "Southlake, TX", "Odessa, TX", "Edinburg, TX", "Victoria, TX", "Belton, TX", "Plainview, TX", "Canyon, TX",
                  
                  "Draper, UT", "Provo, UT", "West Jordan, UT", "Orem, UT", "Saint George, UT", "St. George, UT", "Layton, UT", "Murray, UT", "Salt Lake City, UT", "Ephraim, UT", "Cedar City, UT", "West Haven, UT", "Logan, UT", "Ogden, UT",
                  
                  "Bennington, VT", "Castleton, VT", "Burlington, VT", "Plainfield, VT", "Putney, VT", "Marlboro, VT", "Middlebury, VT", "Montpelier, VT", "Johnson, VT", "Northfield, VT", "Colchester, VT", "Craftsbury Common, VT", "Randolph, VT",
                  
                  "Salem, VA", "Danville, VA", "Hampton, VA", "Bluefield, VA", "Richmond, VA", "Bridgewater, VA", "Virginia Beach, VA", "Lynchburg, VA", "Chesapeake, VA", "Arlington, VA", "Newport News, VA", "Harrisonburg, VA", "Emory, VA", "Fairfax, VA", "Ferrum, VA", "Hampden-Sydney, VA", "Hampden Sydney, VA", "Hampton, VA", "Roanoke, VA", "Vienna, VA", "Farmville, VA", "Staunton, VA", "Norfolk, VA", "Purcellville, VA", "Radford, VA", "Ashland, VA", "Winchester, VA", "Glen Allen, VA", "Buena Vista, VA", "Sweet Briar, VA", "Wise, VA", "Fredericksburg, VA", "University of Richmond, VA", "Falls Church, VA", "Lexington, VA", "Blacksburg, VA", "Petersburg, VA", "Williamsburg, VA",
                  
                  "Seattle, WA", "Kenmore, WA", "Bellevue, WA", "Bellingham, WA", "Bothell, WA", "Ellensburg, WA", "Centralia, WA", "Vancouver, WA", "Lakewood, WA", "Pasco, WA", "Redmond, WA", "Cheney, WA", "Lynnwood, WA", "Tacoma, WA", "Spokane, WA", "Aberdeen, WA", "Auburn, WA", "Toppenish, WA", "Des Moines, WA", "Kirkland, WA", "Longview, WA", "Bremerton, WA", "Port Angeles, WA", "Renton, WA", "Lacey, WA", "Mount Vernon, WA", "Olympia, WA", "Tukwila, WA", "Walla Walla, WA", "College Place, WA", "Pullman, WA", "Wenatchee, WA", "Yakima, WA",
                  
                  "Philippi, WV", "Charles Town, WV", "Mount Hope, WV", "Bethany, WV", "Bluefield, WV", "Athens, WV", "Elkin, WV", "Fairmont, WV", "Glenville, WV", "Huntington, WV", "Vienna, WV", "Keyser, WV", "Salem, WV", "Shepherdstown, WV", "Scott Depot, WV", "Charleston, WV", "Martinsburg, WV", "West Liberty, WV", "Institute, WV", "Morgantown, WV", "Parkersburg, WV", "Beckley, WV", "Buckhannon, WV", "Wheeling, WV",
                  
                  "Milwaukee, WI", "Green Bay, WI", "Beloit, WI", "Wauwatosa, WI", "Waukesha, WI", "Kenosha, WI", "Keshena, WI", "Glendale, WI", "Mequon, WI", "Madison, WI", "Brookfield, WI", "Manitowoc, WI", "Plymouth, WI", "Appleton, WI", "Watertown, WI", "Fond du Lac, WI", "Ashland, WI", "Ripon, WI", "De Pere, WI", "Eau Claire, WI", "La Crosse, WI", "Oshkosh, WI", "Platteville, WI", "River Falls, WI", "Stevens Point, WI", "Menomonie, WI", "Superior, WI", "Whitewater, WI",
                  
                  "Laramie, WY",
                  
                  "Normal, AL", "Montgomery, AL", "Athens, AL", "Auburn, AL", "Birmingham, AL", "Orange Beach, AL", "Florence, AL", "Huntsville, AL", "Jacksonville, AL", "Marion, AL", "Fairfield, AL", "Mobile, AL", "Selma, AL", "Tuscaloosa, AL", "Talladega, AL", "Troy, AL", "Tuskegee, AL", "Daphne, AL", "Montevallo, AL", "Livingston, AL",
                  
                  "Palmer, AK", "Anchorage, AK", "Barrow, AK", "Fairbanks, AK", "Juneau, AK",
                  
                  "Chandler, AZ", "Phoenix, AZ", "Glendale, AZ", "Tempe, AZ", "Mesa, AZ", "Scottsdale, AZ", "Tucson, AZ", "Tsaile, AZ", "Prescott, AZ", "Flagstaff, AZ", "Surprise, AZ", "Sierra Vista, AZ",
                  
                  "Little Rock, AR", "Jonesboro, AR", "Russellville, AR", "Conway, AR", "Hot Springs, AR", "Paragould, AR", "Springdale, AR", "Searcy, AR", "Arkadelphia, AR", "Siloam Springs, AR", "Batesville, AR", "Magnolia, AR", "Fayetteville, AR", "Monticello, AR", "Pine Bluff, AR", "Fort Smith, AR", "Clarkesville, AR", "Walnut Ridge, AR",
                  
                  "Glendale, CA", "San Francisco, CA", "San Diego, CA", "Los Angeles, CA", "Signal Hill, CA", "Lancaster, CA", "Santa Barbara, CA", "Pasadena, CA", "Whitter, CA", "Azusa , CA", "Bakersfield, CA", "Penngrove, CA", "Anaheim, CA", "Beverly Hills, CA", "La Mirada, CA", "Irvine, CA", "Riverside, CA", "Fresno, CA", "Garden Grove, CA", "Valencia, CA", "Berkeley, CA", "Thousand Oaks, CA", "San Luis Obispo, CA", "Pomona, CA", "Vallejo, CA", "Long Beach, CA", "Camarillo, CA", "Chico, CA", "Carson, CA", "Hayward, CA", "Fullerton, CA", "Seaside, CA", "Northridge, CA", "Sacramento, CA", "San Bernardino, CA", "San Marcos, CA", "Turlock, CA", "Santa Ana, CA", "Rancho Cordova, CA", "Orange, CA", "Claremont, CA", "San Jose, CA", "Tarzana, CA", "Cypress, CA", "Ontario, CA", "San Rafael, CA", "Quincy, CA", "Los Altos Hills, CA", "Cerritos, CA", "Hollywood, CA", "San Mateo, CA", "Oakland, CA", "Torrance, CA", "Roseville, CA", "Arcata, CA", "Stockton, CA", "Newport Beach, CA", "Pleasant Hill, CA", "Escondido, CA", "Laguna Beach, CA", "San Dimas, CA", "Loma Linda, CA", "Van Nuys, CA", "Rancho Palos Verdes, CA", "Santa Fe Springs, CA", "Atherton, CA", "Monterey, CA", "Oceanside, CA", "Modesto, CA", "La Jolla, CA", "Burbank, CA", "Fremont, CA", "Belmont, CA", "Costa Mesa, CA", "Angwin, CA", "Palo Alto, CA", "Malibu, CA", "Alhambra, CA", "Whittier, CA", "Emeryville, CA", "Moraga, CA", "Santee, CA", "Visalia, CA", "Santa Clara, CA", "Santa Monica, CA", "Redding, CA", "San Bruno, CA", "Aliso Viejo, CA", "Rohnert Park, CA", "El Cajon, CA", "Stanford, CA", "El Dorado Hills, CA", "Santa Clarita, CA", "Temecula, CA", "Santa Paula, CA", "Los Alamitos, CA", "Davis, CA", "Merced, CA", "Santa Cruz, CA", "La Verne, CA", "Redlands, CA", "Rosemead, CA", "Inglewood, CA", "North Hollywood, CA", "Culver City, CA", "Rocklin, CA",
                  
                  "Alamosa, CO", "Aurora, CO", "Littleton, CO", "Denver, CO", "Colorado Springs, CO", "Fort Collins, CO", "Lakewood, CO", "Grand Junction, CO", "Glenwood Springs, CO", "Golden, CO", "Pueblo, CO", "Westminster, CO", "Durango, CO", "Fort Morgan, CO", "Boulder, CO", "Centennial, CO", "USAF Academy, CO", "Greeley, CO", "Lone Tree, CO", "Gunnison, CO", "United States Air Force Academy, CO",
                  
                  "New Haven, CT", "New Britain, CT", "New London, CT", "Willimantic, CT", "Fairfield, CT", "East Hartford, CT", "Cromwell, CT", "Hamden, CT", "Waterbury, CT", "Hamden, CT", "Hartford, CT", "Bridgeport, CT", "Storrs, CT", "Groton, CT", "Stamford, CT", "West Hartford, CT", "West Haven, CT", "Middletown, CT", "Danbury, CT",
                  
                  "Dover, DE", "Wilmington, DE", "Newark, DE", "New Castle, DE",
                  
                  "Miami, FL", "Orlando, FL", "Fort Lauderdale, FL", "Ave Maria, FL", "Leesburg, FL", "Daytona Beach, FL", "Delray Beach, FL", "Altamonte Springs, FL", "Jacksonville, FL", "Marianna, FL", "Gainesville, FL", "Ocala, FL", "Ormond Beach, FL", "Miramar, FL", "Cocoa, FL", "Saint Petersburg, FL", "St. Petersburg, FL", "Boca Raton, FL", "Tampa, FL", "St. Augustine, FL", "Saint Augustine, FL", "Tallahassee, FL", "Temple Terrace, FL", "Lake City, FL", "Fort Myers, FL", "Melbourne, FL", "Hialeah, FL", "Lakeland, FL", "Winter Park, FL", "Panama City, FL", "West Palm Beach, FL", "Hobe Sound, FL", "Naples, FL", "Fort Pierce, FL", "North Miami, FL", "Kissimmee, FL", "Pembroke Pines, FL", "Miami Springs, FL", "Doral, FL", "Sarasota, FL", "Madison, FL", "Niceville, FL", "Lake Worth, FL", "New Port Richey, FL", "Pensacola, FL", "Winter Haven, FL", "Ocala, FL", "Lake Mary, FL", "Palatka, FL", "Saint Leo, FL", "St. Leo, FL", "Largo, FL", "Sanford, FL", "Deerfield Beach, FL", "Avon Park, FL", "Royal Palm Beach, FL", "Clearwater, FL", "Miami Gardens, FL", "Bradenton, FL", "DeLand, FL", "Graceville, FL", "Key West, FL", "Trinity, FL", "Lauderhill, FL", "Coral Gables, FL", "Lake Wales, FL", "Babson Park, FL",
                  
                  "Tifton, GA", "Decatur, GA", "Albany, GA", "Cuthbert, GA", "Atlanta, GA", "Augusta, GA", "Mount Berry, GA", "Gainesville, GA", "Mount Vernon, GA", "Morrow, GA", "Brunswick, GA", "Columbus, GA", "Lookout Mountain, GA", "Dalton, GA", "Swainsboro, GA", "Franklin Springs, GA", "Fort Valley, GA", "Milledgeville, GA", "Lawrenceville, GA", "Rome, GA", "Statesboro, GA", "Americus, GA", "Barnesville, GA", "Kennesaw, GA", "Lagrange, GA", "Marietta, GA", "Lithonia, GA", "Macon, GA", "Kings Bay, GA", "Demorest, GA", "West Point, GA", "Waleska, GA", "Savannah, GA", "Douglas, GA", "Thomasville, GA", "Toccoa Falls, GA", "Cleveland , GA", "Athens, GA", "Dahlonega, GA", "Carrollton, GA", "Valdosta, GA", "Young Harris, GA",
                  
                  "Laie, HI", "Honolulu, HI", "Hilo, HI", "Kahului, HI", "Kapolei, HI",
                  
                  "Boise, ID", "Rexburg, ID", "Twin Falls, ID", "Pocatello, ID", "Lewiston, ID", "Moscow, ID", "Nampa, ID", "Idaho Falls, ID", "Caldwell, ID",
                  
                  "Hoffman Estates, IL", "Chicago, IL", "Rock Island, IL", "Aurora, IL", "Lisle, IL", "Carlinville, IL", "Quincy, IL", "Peoria, IL", "Downers Grove, IL", "Addison, IL", "Mount Prospect, IL", "River Forest, IL", "Naperville, IL", "Charleston, IL", "Elmhurst, IL", "Eureka, IL", "University Park, IL", "Greenville, IL", "Skokie, IL", "Jacksonville, IL", "Normal, IL", "Bloomington, IL", "Elgin, IL", "Galesburg, IL", "Danville, IL", "Romeoville, IL", "Lincoln, IL", "Lebanon, IL", "Monmouth, IL", "Lombard, IL", "Dekalb, IL", "Bridgeview, IL", "Evanston, IL", "Bourbannais, IL", "Elsah, IL", "Rockford, IL", "Carbondale, IL", "Edwardsville, IL", "Springfield, IL", "Palos Heights, IL", "Deerfield, IL", "Champaign, IL", "Urbana, IL", "Joliet, IL", "Macomb, IL", "Wheaton, IL",
                  
                  "Indianapolis, IN", "Anderson, IN", "Crawfordsville, IN", "Muncie, IN", "Mishawaka, IN", "Whiting, IN", "Greencastle, IN", "Merrillville, IN", "Goshen, IN", "Richmond, IN", "Franklin, IN", "Winona Lake, IN", "Hanover, IN", "Notre Dame, IN", "Huntington, IN", "Fort Wayne, IN", "Terre Haute, IN", "Bloomington, IN", "Kokomo, IN", "Gary, IN", "South Bend, IN", "New Albany, IN", "Marion, IN", "North Manchester, IN", "Jeffersonville, IN", "Oakland City, IN", "Hammond, IN", "West Lafayette, IN", "Saint Mary of the Woods, IN", "St. Mary of the Woods, IN", "Upland, IN", "Angola, IN", "Westfield, IN", "Evansville, IN", "Valparaiso, IN", "Greendale, IN", "Vincennes, IN",
                  
                  "Waterloo, IA", "Sioux City, IA", "Storm Lake, IA", "Pella, IA", "Dubuque, IA", "Cedar Rapids, IA", "Mount Vernon, IA", "Epworth, IA", "Sioux Center, IA", "Des Moines, IA", "Ankeny, IA", "Lamoni, IA", "Grinnell, IA", "Davenport, IA", "Ames, IA", "Mount Pleasant, IA", "Decorah, IA", "Fairfield, IA", "Orange City, IA", "Kalona, IA", "Indianola, IA", "Iowa City, IA", "Fayette, IA", "Forest City, IA", "Oskaloosa, IA", "Waverly, IA",
                  
                  "Baldwin City, KS", "Haviland, KS", "Atchison, KS", "Lindsborg, KS", "North Newton, KS", "McPherson, KS", "Overland Park, KS", "Kansas City, KS", "Emporia, KS", "Hays, KS", "Wichita, KS", "Lenexa, KS", "Lawrence, KS", "Hesston, KS", "Manhattan, KS", "Salina, KS", "Olathe, KS", "Garden City, KS", "Ottawa, KS", "Pittsburg, KS", "Topeka, KS", "Winfield, KS", "Sterling, KS", "Hillsboro, KS", "Leavenworth, KS",
                  
                  "Pippa Passes, KY", "Lexington, KY", "Wilmore, KY", "Florence, KY", "Louisville, KY", "Berea, KY", "Owensboro, KY", "Campbellsville, KY", "Danville, KY", "Pineville, KY", "Richmond, KY", "Georgetown, KY", "Bowling Green, KY", "Grayson, KY", "Jackson, KY", "Frankfort, KY", "Owensboro, KY", "Columbia, KY", "Midway, KY", "Moorehead, KY", "Murray, KY", "Highland Heights, KY", "Crestview Hills, KY", "Lexington, KY", "Barbourville, KY", "Pikeville, KY", "Williamsburg, KY",
                  
                  "Shreveport, LA", "Jefferson, LA", "New Orleans, LA", "Baton Rouge, LA", "Grambling, LA", "Kenner, LA", "Pineville, LA", "Ruston, LA", "Lake Charles, LA", "Thibodaux, LA", "Natchitoches, LA", "St. Benedict, LA", "Saint Benedict, LA", "Hammond, LA", "Lafayette, LA", "Monroe, LA",
                  
                  "Lewiston, ME", "Bangor, ME", "Brunswick, ME", "Waterville, ME", "Bar Harbor, ME", "Portland, ME", "Castine, ME", "Standish, ME", "Unity, ME", "Orono, ME", "Augusta, ME", "Farmington, ME", "Fort Kent, ME", "Machias, ME", "Presque Isle, ME", "Biddleford, ME",
                  
                  "Baltimore, MD", "Bowie, MD", "Laurel, MD", "Frostburg, MD", "Frederick, MD", "Capitol Heights, MD", "Westminster, MD", "Emmitsburg, MD", "Salisbury, MD", "Annapolis, MD", "St. Mary’s City, MD", "Saint Mary’s City, MD", "Stevenson, MD", "Suitland, MD", "Townson, MD", "Princess Anne, MD", "Adelphi, MD", "College Park, MD", "Takoma Park, MD", "Chestertown, MD", "Silver Spring, MD",
                  
                  "Cambridge, MA", "Boston, MA", "Springfield, MA", "Amherst, MA", "Paxton, MA", "Worcester, MA", "Wellesley, MA", "Great Barrington, MA", "Longmeadow, MA", "Waltham, MA", "Chestnut Hill, MA", "Bridgewater, MA", "Chicopee, MA", "Milton, MA", "Franklin, MA", "Quincy, MA", "Beverly, MA", "Fitchburg, MA", "Framingham, MA", "Needham, MA", "Wenham, MA", "Brookline, MA", "Newton Centre, MA", "Newton, MA", "North Adams, MA", "Buzzards Bay, MA", "North Andover, MA", "South Hadley, MA", "Dudley, MA", "Haverhill, MA", "Weston, MA", "Brighton, MA", "Salem, MA", "Northampton, MA", "Easton, MA", "Medford, MA", "North Dartmouth, MA", "Lowell, MA", "Norton, MA", "Williamstown, MA",
                  
                  "Adrian, MI", "Albion, MI", "Alma, MI", "Alpena, MI", "Berrien Springs, MI", "Grand Rapids, MI", "Owosso, MI", "Brimley, MI", "Mount Pleasant, MI", "Troy, MI", "Howell, MI", "Detroit, MI", "Ann Arbor, MI", "Ypsilanti, MI", "Big Rapids, MI", "Hancock, MI", "Wyoming, MI", "Allendale, MI", "Lansing, MI", "Dearborn, MI", "Hillsdale, MI", "Holland, MI", "Jackson, MI", "Kalamazoo, MI", "Flint, MI", "Benton Harbor, MI", "Sault Ste Marie, MI", "Southfield, MI", "Livonia, MI", "East Lansing, MI", "Houghton, MI", "Marquette, MI", "Traverse City, MI", "Midland, MI", "Rochester Hills, MI", "Olivet, MI", "University Center, MI", "Novi, MI", "Spring Arbor, MI", "Southfield, MI", "Oak Park, MI",
                  
                  
                  "Chicago, IL--IN", "Washington, DC--VA--MD", "New York--Newark, NY--NJ--CT", "Cincinnati, OH--KY--IN", "Las Vegas--Henderson, NV", "Kansas City, MO--KS", "Los Angeles--Long Beach--Anaheim, CA", "Charleston--North Charleston, SC", "Springfield, MA--CT", "Charles Town--Ranson, WV", "Richmond, IN--OH", 
                  "St. Louis, MO--IL", "Fayetteville--Springdale--Rogers, AR--MO", "Conroe--The Woodlands, TX", "Murrieta--Temecula--Menifee, CA", "Minneapolis--St. Paul, MN--WI", "Denver--Aurora, CO", "Palm Coast--Daytona Beach--Port Orange, FL", "Charlotte, NC--SC", "San Francisco--Oakland, CA", 
                  "Ogden--Layton, UT", "Louisville/Jefferson County, KY--IN", "Memphis, TN--MS--AR", "Tampa--St. Petersburg, FL", "Chattanooga, TN--GA", "Portland, OR--WA", "Bridgeport--Stamford, CT--NY", "Philadelphia, PA--NJ--DE--MD", "Dallas--Fort Worth--Arlington, TX", "Bloomsburg--Berwick, PA", "Toledo, OH--MI", "Allentown, PA--NJ", 
                  "Worcester, MA--CT", "Grand Forks, ND--MN", "Phoenix--Mesa, AZ", "Boston, MA--NH--RI", "Norwich--New London, CT--RI", "El Paso, TX--NM", "Omaha, NE--IA", "South Bend, IN--MI", "Pensacola, FL--AL", "Riverside--San Bernardino, CA", "Providence, RI--MA", "Poughkeepsie--Newburgh, NY--NJ", "Albany--Schenectady, NY", "Huntington, WV--KY--OH", 
                  "Sarasota--Bradenton, FL", "Columbus, GA--AL", "Fargo, ND--MN", "Kenosha, WI--IL", "Kennewick--Pasco, WA", "Youngstown, OH--PA", "Olympia--Lacey, WA", "Reno, NV--CA", "Sioux City, IA--NE--SD", "College Station--Bryan, TX", "Denton--Lewisville, TX", "Weirton--Steubenville, WV--OH--PA", "Salt Lake City--West Valley City, UT", "Fort Smith, AR--OK", "Walla Walla, WA--OR",
                  "Monessen--California, PA", "Staunton--Waynesboro, VA", "Westminster--Eldersburg, MD", "Lancaster--Palmdale, CA", "Portsmouth, OH--KY", "Salisbury, MD--DE", "Danbury, CT--NY", "East Liverpool, OH--WV--PA", 
                  "Marietta, OH--WV", "Lorain--Elyria, OH", "Bloomington--Normal, IL", "Clarksville, TN--KY", "St. Joseph, MO--KS", "New Philadelphia--Dover, OH", "Nashua, NH--MA", "Seaside--Monterey, CA", "Prescott Valley--Prescott, AZ", "Davenport, IA--IL", "Benton Harbor--St. Joseph--Fair Plain, MI", 
                  "Milton--Lewisburg, PA", "Bristol--Bristol, TN--VA", "Provo--Orem, UT", "South Lyon--Howell, MI", "Palm Bay--Melbourne, FL", "Danville, VA--NC", "Wheeling, WV--OH", "Bluefield, WV--VA", "Atchison, KS--MO", "Marinette--Menominee, WI--MI", "Lewiston, ID--WA",
                  "East Stroudsburg, PA--NJ", "Evansville, IN--KY", "Longview, WA--OR", "Duluth, MN--WI", "Klamath Falls--Altamont, OR", "La Crosse, WI--MN", "Leominster--Fitchburg, MA", "Keyser, WV--MD", "Siloam Springs, AR--OK", "Leesburg--Eustis--Tavares, FL", "Emmitsburg, MD--PA", "Beloit, WI--IL", 
                  "Dubuque, IA--IL", "Arcata--McKinleyville, CA", "Wendell--Zebulon, NC", "Parkersburg, WV--OH", "Lake Jackson--Angleton, TX", "Lebanon--Hanover, NH--VT", "Sebring--Avon Park, FL", "Barre--Montpelier, VT", "Bradford, PA--NY", "Texarkana--Texarkana, TX--AR", 
                  "Daphne--Fairhope, AL", "Monmouth--Independence, OR", "Laie--Hauula, HI", "North Adams, MA--VT", "Dunkirk--Fredonia, NY", "Norton--Wise, VA", "Alma--St. Louis, MI", "Lawrenceburg--Greendale--Aurora, IN", "Incline Village, NV--CA", "Shepherdstown, WV--MD"

                  )

```

```{r}
data <- data |> 
  mutate(region = case_when(State %in% c("CT", "ME", "MA", "NH", "RI", "VT", "NJ", "NY", "PA") ~ "Northeast",
                            State %in% c("IN", "IL", "MI", "OH", "WI", "MN", "IA","MO", "KS", "NE", "ND", "SD") ~ "Midwest",
                            State %in% c("DE", "DC", "FL", "GA", "MD", "NC", "SC", "VA", "WV", "AL", "KY", "MI", "TN", "AR", "LA", "OK", "TX") ~ "South",
                            State %in% c("AZ", "CO", "ID", "NM", "MT", "UT", "NV", "WY", "AK", "CA", "WA", "OR", "HI") ~ "West"),
         district = case_when(State %in% c("CT", "ME", "MA", "NH", "RI", "VT") ~ "New England",
                              State %in% c("NJ", "NY", "PA") ~ "Middle Atlantic",
                              State %in% c("IN", "IL", "MI", "OH", "WI") ~ "East North Central",
                              State %in% c("MN", "IA","MO", "KS", "NE", "ND", "SD") ~ "West North Central",
                              State %in% c("DE", "DC", "FL", "GA", "MD", "NC", "SC", "VA", "WV") ~ "South Atlantic",
                              State %in% c("AL", "KY", "MI", "TN") ~ "East South Central",
                              State %in% c("AR", "LA", "OK", "TX") ~ "West South Central",
                              State %in% c("AZ", "CO", "ID", "NM", "MT", "UT", "NV", "WY") ~ "Mountain",
                              State %in% c("AK", "CA", "WA", "OR", "HI") ~ "Pacific"))

```


## Raw Data

```{r}
data <- data |>
  mutate(
        college_town = if_else(UA_NAME %in% college_towns, 1, 0))

data

```
## Tidying the Data

```{r}
al <- data |> 
  filter(State == "AL") 

unique(al$UA_NAME)

al_names <- c("Valley--Lanett, AL--GA", "Tuskegee, AL", "Albertville, AL", "Sylacauga, AL", "Atmore, AL", "Jasper, AL",          "Robertsdale, AL", "Union Springs, AL", "Oneonta, AL", "Centre, AL", "Troy, AL", "Scottsboro, AL", "Pell City, AL",     "Daphne--Fairhope, AL", "Moundville, AL", "Piedmont, AL", "Brent, AL", "Monroeville, AL", "Roanoke, AL",                "Arab, AL", "Hamilton, AL", "Eufaula, AL--GA", "Hanceville, AL", "Bay Minette, AL", "Haleyville, AL", "Wetumpka, AL", "Geneva, AL", "Ozark, AL", "Opp, AL", "Talladega, AL", "Andalusia, AL", "Moulton, AL", "Alexander City, AL", "Thomasville, AL", "Greenville, AL", "Tallassee, AL", "Jackson, AL", "Grand Bay, AL", "Clanton, AL", "Columbiana, AL", "Hazel Green, AL", "Priceville, AL","Evergreen, AL","Springville, AL", "Selma, AL", "Fayette, AL","Auburn, AL", "Birmingham, AL", "Cullman, AL", "Enterprise, AL", "Fort Payne, AL", "Huntsville, AL", "Florence, AL", "Russellville, AL", "Mobile, AL", "Athens, AL", "Demopolis, AL", "Anniston--Oxford, AL", "Montgomery, AL", "Tuscaloosa, AL", "Sumiton, AL", "Dothan, AL","Gadsden, AL", "Brewton, AL", "Headland, AL", "Foley, AL", "Decatur, AL")
```

```{r} 
ak <- data |> 
  filter(State == "AK") 

unique(ak$UA_NAME)

ak_names <- c("Anchorage, AK", "Fairbanks, AK", "Bethel, AK", "Kodiak, AK", "Lakes--Knik-Fairview--Wasilla, AK", "Anchorage Northeast, AK", "Soldotna, AK", "Nome, AK", "Juneau, AK", "Kenai, AK","Ketchikan, AK","Sitka, AK", "Barrow, AK", "Eielson AFB, AK", "Kotzebue, AK")

```

```{r}
az <- data |> 
  filter(State == "AZ") 

unique(az$UA_NAME)

az_names <- c("Tucson, AZ", "Phoenix--Mesa, AZ", "Yuma, AZ--CA","Casa Grande, AZ", "Avondale--Goodyear, AZ", "Prescott Valley--Prescott, AZ", "Eagar, AZ", "Wickenburg, AZ", "Nogales, AZ", "Sierra Vista, AZ", "Bullhead City, AZ--NV", "Flagstaff, AZ", "Sahuarita--Green Valley, AZ", "Winslow, AZ", "Kingman, AZ", "Lake Havasu City, AZ", "Chinle, AZ", "Show Low, AZ", "Douglas, AZ", "Cottonwood--Verde Village, AZ", "Tuba City, AZ", "Village of Oak Creek (Big Park), AZ", "Coolidge, AZ", "Safford, AZ", "Picture Rocks, AZ", "Chino Valley, AZ", "Page, AZ", "Buckeye, AZ", "Maricopa, AZ", "Eloy, AZ", "Payson, AZ", "San Luis, AZ", "Quartzsite, AZ", "Florence, AZ", "Kayenta, AZ", "St. Johns, AZ", "Globe, AZ", "Sedona, AZ", "Vail, AZ", "Window Rock, AZ--NM", "Lake of the Woods--Pinetop-Lakeside, AZ", "Holbrook, AZ", "Williams, AZ", "Snowflake, AZ", "Camp Verde, AZ", "Willcox, AZ", "Parker, AZ--CA", "Benson, AZ", "Somerton, AZ", "Arizona City, AZ", "Bisbee, AZ", "Marana West, AZ", "Clifton, AZ", "Estrella, AZ", "Lake Montezuma, AZ", "San Manuel, AZ", "Ajo, AZ", "Colorado City, AZ--UT", "Whiteriver, AZ", "Corona de Tucson, AZ", "Superior, AZ", "San Carlos, AZ", "Avra Valley, AZ")

```

```{r}
ar <- data |> 
  filter(State == "AR") 

unique(ar$UA_NAME)

ar_names <- c("Little Rock, AR", "McGehee, AR", "Fayetteville--Springdale--Rogers, AR--MO", "Searcy, AR", "Osceola, AR", "Conway, AR", "Brinkley, AR", "Mountain Home, AR", "Fort Smith, AR--OK", "Beebe, AR", "Waldron, AR", "Ashdown, AR", "Clarksville, AR", "Mena, AR", "Jonesboro, AR", "Walnut Ridge, AR", "Camden, AR", "Russellville, AR", "El Dorado, AR", "Corning, AR", "Hot Springs, AR", "Siloam Springs, AR--OK", "Harrison, AR", "Morrilton, AR","Lake Village, AR", "Pine Bluff, AR","Batesville, AR", "Paragould, AR","Arkadelphia, AR", "Newport, AR", "Hamburg, AR", "Forrest City, AR", "Greenwood, AR","Wynne, AR","Heber Springs, AR", "Magnolia, AR", "Marianna, AR", "Blytheville, AR", "Dumas, AR","Hot Springs Village, AR", "Hope, AR", "Warren, AR", "Crossett, AR", "Nashville, AR","Berryville, AR","Helena-West Helena, AR","Malvern, AR","Ozark, AR","Bald Knob, AR", "England, AR","Paris, AR", "Fordyce, AR", "Greenbrier, AR","Trumann, AR","Manila, AR", "Sheridan, AR", "DeWitt, AR", "Monticello, AR", "Stuttgart, AR", "Booneville, AR", "De Queen, AR", "Pocahontas, AR", "Prescott, AR", "Prairie Grove, AR", "Green Forest, AR", "Piggott, AR", "Cherokee Village, AR","Lonoke, AR")

```

```{r}
ca <- data |> 
  filter(State == "CA") 

unique(ca$UA_NAME)

ca_names <- c("El Paso de Robles (Paso Robles)--Atascadero, CA", "Los Angeles--Long Beach--Anaheim, CA", "Petaluma, CA", "San Diego, CA", "Barstow, CA", "Mission Viejo--Lake Forest--San Clemente, CA", "Murrieta--Temecula--Menifee, CA", "San Francisco--Oakland, CA", "Santa Clarita, CA", "Porterville, CA", "Sacramento, CA", "Woodlake, CA", "Camarillo, CA", "Fresno, CA", "Bakersfield, CA", "Concord, CA", "Riverside--San Bernardino, CA", "Indio--Cathedral City, CA","Modesto, CA", "Redding, CA", "Hemet, CA", "Victorville--Hesperia, CA", "Sonora--Jamestown--Phoenix Lake, CA", "Mount Shasta--Weed, CA", "California City, CA", "Lindsay, CA", "Madera, CA", "Lancaster--Palmdale, CA", "Santa Maria, CA", "Vallejo, CA", "Lake Arrowhead--Crestline, CA", "Sonoma, CA", "Antioch, CA", "Santa Barbara, CA", "Colfax, CA", "Thousand Oaks, CA", "Gilroy--Morgan Hill, CA", "Stockton, CA","Corning, CA","San Jose, CA","Turlock, CA","Oxnard, CA", "Santa Rosa, CA", "Orange Cove, CA", "Seaside--Monterey, CA", "Fortuna, CA", "Hanford, CA", "Davis, CA", "Santa Cruz, CA", "Crescent City, CA", "Salinas, CA", "Portola, CA", "Mammoth Lakes, CA", "Dixon, CA", "Lodi, CA", "Fairfield, CA", "Lompoc, CA", "Chowchilla, CA", "Big Bear City, CA", "Shafter, CA", "Oroville, CA", "Watsonville, CA", "Live Oak (Sutter County), CA", "Livermore, CA", "Yuba City, CA", "Bishop, CA", "Arroyo Grande--Grover Beach, CA", "Simi Valley, CA", "Discovery Bay, CA","Rosamond, CA","Auburn--North Auburn, CA","Reedley--Dinuba, CA","Manteca, CA","Vacaville, CA","Firebaugh, CA","Napa, CA","Bonadelle Ranchos-Madera Ranchos, CA","Tracy, CA","Cloverdale, CA","Alturas, CA","Hollister, CA", "Arvin, CA","Visalia, CA","Chico, CA","Ramona, CA", "Morro Bay--Los Osos, CA", "Willits, CA", "Fort Irwin, CA", "El Centro--Calexico, CA", "Cottonwood, CA","Placerville--Diamond Springs, CA", "Gridley, CA", "Ridgecrest, CA", "Ukiah, CA", "Needles, CA--AZ", "Grass Valley, CA", "Santa Paula, CA", "Rio Vista, CA", "Arcata--McKinleyville, CA", "Selma, CA","Merced, CA", "Woodland, CA", "Williams, CA","Wasco, CA", "McFarland, CA", "Yreka, CA", "Los Banos, CA", "Brawley, CA", "Angels, CA","Delano, CA","Susanville, CA","Hidden Valley Lake, CA","Willows, CA", "Clearlake, CA", "Orosi, CA", "Parlier, CA", "Patterson, CA", "Fillmore, CA", "Jackson, CA", "Twentynine Palms, CA", "Paradise, CA", "East Quincy, CA", "Red Bluff, CA", "Half Moon Bay, CA", "Eureka, CA", "Lakeport, CA", "San Luis Obispo, CA", "Truckee, CA", "Mendota, CA", "Dos Palos, CA", "Blythe, CA--AZ", "Galt, CA", "Gustine, CA", "Kerman, CA", "Fort Bragg, CA", "Escalon, CA","South Lake Tahoe, CA--NV","Waterford, CA","Phelan, CA","Taft, CA", "Mojave, CA","Guerneville, CA","Avenal, CA", "Colusa, CA", "Tehachapi--Golden Hills, CA", "Sanger, CA",  "Solvang--Buellton--Santa Ynez, CA", "King City, CA" , "Newman, CA", "Tipton, CA","Yucca Valley, CA", "Corcoran, CA","Desert Hot Springs, CA", "Orland, CA", "Gonzales, CA", "Hilmar-Irwin, CA","Winters, CA","Ione, CA","Coalinga, CA", "Rancho Calaveras--Valley Springs, CA", "Guadalupe, CA", "Greenfield, CA", "Riverdale, CA", "Soledad, CA", "Wheatland, CA", "Nipomo, CA", "Lake Wildwood, CA", "Earlimart, CA", "Burney, CA", "Lemoore Station, CA", "Oakhurst, CA", "Holtville, CA", "Twentynine Palms Base, CA", "Vandenberg AFB, CA", "Running Springs, CA", "St. Helena, CA","Mecca, CA", "Rio Dell, CA", "Lake of the Pines, CA", "San Joaquin, CA", "Wrightwood, CA", "Cambria, CA", "Huron, CA", "Forestville, CA", "Carmel Valley Village, CA", "Avalon, CA", "Calistoga, CA", "Rancho Murieta, CA", "Yountville, CA", "Los Molinos, CA", "Silver Lakes, CA", "Frazier Park, CA", "Lake Rancho Viejo, CA", "Calipatria, CA","Arbuckle, CA","Terra Bella, CA","Kelseyville, CA", "Poplar-Cotton Center, CA","Clearlake Riviera, CA", "Esparto, CA", "Lake Los Angeles, CA", "Planada, CA", "Richgrove, CA")

```

```{r}
co <- data |> 
  filter(State == "CO") 

unique(co$UA_NAME)

co_names <- c("Denver--Aurora, CO", "Lafayette--Louisville--Erie, CO", "Colorado Springs, CO", "Woodland Park, CO", "Pagosa Springs, CO", "Grand Junction, CO", "Gypsum, CO", "Rifle, CO", "Pueblo, CO", "Boulder, CO","Fort Collins, CO", "Eagle, CO", "Estes Park, CO", "Johnstown, CO", "Burlington, CO", "Delta, CO", "Edwards, CO", "Leadville, CO", "Fort Morgan, CO", "Yuma, CO", "Breckenridge, CO", "Longmont, CO", "Brush, CO", "Cañon City, CO", "Silverthorne--Frisco, CO", "Air Force Academy, CO", "Greeley, CO", "Wellington, CO", "Buena Vista, CO", "New Castle, CO", "Steamboat Springs, CO", "Glenwood Springs, CO", "Roxborough Park, CO", "Lamar, CO", "Durango, CO","Montrose, CO","Firestone--Frederick, CO", "Walsenburg, CO", "Carbondale, CO", "Alamosa, CO", "La Junta, CO","Rocky Ford, CO","Vail, CO", "Gunnison, CO", "Fort Lupton, CO","Fraser, CO","Battlement Mesa, CO","Cedaredge, CO","Sterling, CO", "Florence, CO", "Monte Vista, CO", "Lochbuie, CO", "Craig, CO", "Basalt--El Jebel, CO", "Trinidad, CO", "Salida, CO", "Eaton, CO", "Cortez, CO", "Evergreen, CO", "Las Animas, CO", "Aspen, CO", "Bayfield, CO", "Silt, CO", "Severance, CO")

```

```{r}
ct <- data |> 
  filter(State == "CT") 

unique(ct$UA_NAME)

ct_names <- c("New Haven, CT", "Hartford, CT", "Bridgeport--Stamford, CT--NY", "Norwich--New London, CT--RI","Danbury, CT--NY", "Torrington, CT", "Waterbury, CT", "Willimantic, CT", "Lake Pocotopaug--East Hampton, CT", "Colchester, CT", "Jewett City, CT", "Litchfield, CT", "Stafford Springs, CT", "Moodus, CT")

```

```{r}
de <- data |> 
  filter(State == "DE") 

unique(de$UA_NAME)

de_names <- c("Lewes, DE", "Millsboro, DE","Milton, DE", "Dover, DE", "Georgetown, DE", "Long Neck, DE", "Ocean View, DE", "Harrington, DE","Middletown, DE","Milford, DE", "Bridgeville, DE")

```

```{r}
dc <- data |>
  filter(State == "DC")

unique(dc$UA_NAME)

dc_names <- "Washington, DC--VA--MD"

```

```{r}
fl <- data |>
  filter(State == "FL")

unique(fl$UA_NAME)

fl_names <- c("Cape Coral, FL", "Miami, FL", "Palm Coast--Daytona Beach--Port Orange, FL", "Lady Lake--The Villages, FL", "Winter Haven, FL", "Tampa--St. Petersburg, FL", "Port St. Lucie, FL", "Okeechobee--Taylor Creek, FL", "Orlando, FL", "Jacksonville, FL", "Pensacola, FL--AL","Sarasota--Bradenton, FL","North Port--Port Charlotte, FL", "Ocala, FL", "Key Largo, FL", "Bonita Springs, FL", "Tallahassee, FL", "Starke, FL", "Panama City, FL", "Deltona, FL", "Kissimmee, FL", "Lakeland, FL",  "Sebastian--Vero Beach South--Florida Ridge, FL", "Gainesville, FL", "Lake City, FL", "Palm Bay--Melbourne, FL", "Fort Walton Beach--Navarre--Wright, FL", "Sugarmill Woods, FL", "Titusville, FL", "Perry, FL", "St. Augustine, FL", "Bonifay, FL", "Poinciana, FL", "Spring Hill, FL", "Quincy, FL", "Homosassa Springs--Beverly Hills--Citrus Springs, FL", "Key West, FL", "Crystal River, FL", "Yulee, FL", "Live Oak, FL", "Leesburg--Eustis--Tavares, FL", "Nassau Village-Ratliff, FL", "Woodville, FL", "Four Corners, FL", "Moore Haven, FL", "Zephyrhills, FL", "Sebring--Avon Park, FL", "Marianna, FL", "Lake Placid, FL", "Orangetree, FL", "Indiantown, FL", "Bushnell, FL", "Clewiston, FL", "LaBelle--Port LaBelle, FL", "Cross City, FL", "Palatka, FL", "High Springs, FL", "Arcadia--Southeast Arcadia, FL", "Pahokee, FL", "Fernandina Beach, FL", "Keystone Heights, FL", "Belle Glade, FL", "Chipley, FL", "Immokalee, FL", "Williston, FL", "Crestview, FL", "Jasper, FL", "De Funiak Springs, FL", "Frostproof, FL", "World Golf Village, FL", "Havana, FL", "Madison, FL", "Graceville, FL", "Macclenny, FL", "Chattahoochee, FL", "Apalachicola, FL", "Santa Rosa Beach, FL", "Lake Butler, FL", "Crescent City, FL", "Marathon, FL", "Blountstown, FL", "Interlachen, FL", "Alachua, FL", "Trenton, FL", "Port St. Joe, FL", "Crawfordville, FL", "Fort Meade, FL", "Wauchula, FL", "Marion Oaks, FL", "Lake Bryant, FL", "Century, FL--AL", "Big Pine Key, FL", "Fellsmere, FL", "Panama City Northeast, FL","Rainbow Lakes Estates, FL", "Lake Panasoffkee, FL", "Burnt Store Marina, FL", "Crooked Lake Park, FL", "Ridge Manor, FL")

```

```{r}
ga <- data |>
  filter(State == "GA")

unique(ga$UA_NAME)

ga_names <- c("Milledgeville, GA", "Atlanta, GA", "Dublin, GA", "Savannah, GA", "Waycross, GA", "Ocilla, GA", "Athens-Clarke County, GA", "Gainesville, GA", "Columbus, GA--AL", "Macon, GA", "St. Marys--Kingsland, GA", "Moultrie, GA", "Augusta-Richmond County, GA--SC", "Jesup, GA", "Valdosta, GA", "Metter, GA", "Brunswick, GA", "Blakely, GA", "Albany, GA", "Winder, GA","Homerville, GA", "Trenton, GA", "Cordele, GA","Jasper, GA", "Douglas, GA", "Nashville, GA", "Tifton, GA", "Dalton, GA", "LaGrange, GA", "Manchester, GA", "Folkston, GA", "Warner Robins, GA", "Vidalia, GA", "Cochran, GA", "Waynesboro, GA", "Thomasville, GA", "Rome, GA", "Hinesville, GA", "Sparta, GA", "Leesburg, GA", "Montezuma, GA", "Eastman, GA", "Clayton, GA","Louisville, GA", "Carrollton, GA", "Americus, GA", "Unadilla, GA","Lake Park, GA","Hartwell, GA", "Summerville, GA", "Monroe, GA", "Forsyth, GA", "Swainsboro, GA","Rockmart, GA", "Cleveland, GA","Camilla, GA", "Soperton, GA", "Barnesville, GA", "Calhoun, GA", "Cornelia--Baldwin, GA", "Sylvester, GA","Pelham, GA","Cartersville, GA","Harlem, GA","Toccoa, GA","Dahlonega, GA", "Thomaston, GA", "Elberton, GA", "St. Simons, GA", "Washington, GA", "Glennville, GA", "Jackson, GA", "Statesboro, GA", "Donalsonville, GA", "Rincon, GA", "Sylvania, GA", "Bainbridge, GA", "Fitzgerald, GA", "Blackshear, GA","Cairo, GA","Bremen, GA", "Quitman, GA", "McRae, GA", "Monticello, GA", "Lakeland, GA","Commerce, GA","Sandersville, GA", "Cedartown, GA", "Hazlehurst, GA", "Jefferson, GA", "Wrightsville, GA", "Adel, GA", "Thomson, GA", "Baxley, GA", "Hawkinsville, GA", "Claxton, GA", "Millen, GA", "Cuthbert, GA", "Dawson, GA", "Social Circle, GA", "Madison, GA", "Alma, GA", "LaFayette, GA", "Fort Valley, GA", "Gray, GA", "Ellijay, GA", "Reidsville, GA", "Eatonton, GA", "Ashburn, GA", "Springfield, GA","Darien, GA", "Royston, GA", "Tybee Island, GA", "Vienna, GA", "Greensboro, GA", "Lula, GA", "Grantville, GA", "Buckhead (Bryan County), GA", "Nelson, GA")

```

```{r}
hi <- data |>
  filter(State == "HI")

unique(hi$UA_NAME)

hi_names <- c("Urban Honolulu, HI", "Lihue, HI", "Kailua (Honolulu County)--Kaneohe, HI", "Kalaheo, HI", "Kahului, HI", "Kilauea, HI", "Kihei, HI", "Hilo, HI", "Kailua (Hawaii County)--Holualoa, HI", "Pukalani--Makawao--Haiku-Pauwela, HI","Kekaha, HI", "Lahaina, HI", "Kapaa, HI", "Laie--Hauula, HI", "Waimea (Hawaii County), HI", "Captain Cook, HI", "Haleiwa--Waialua--Pupukea, HI", "Hawaiian Paradise Park, HI", "Kapaau, HI", "Honokaa, HI", "Princeville, HI", "Lanai City, HI")

```

```{r}
id <- data |>
  filter(State == "ID")

unique(id$UA_NAME)

id_names <- c("Coeur d'Alene, ID", "Boise City, ID", "Hailey, ID", "Bonners Ferry, ID", "Idaho Falls, ID", "Burley, ID", "Filer, ID", "Shelley, ID", "Pocatello, ID", "Rupert, ID","Grangeville, ID", "Mountain Home, ID","Nampa, ID","Sandpoint, ID", "St. Anthony, ID", "Twin Falls, ID", "Rexburg, ID","Weiser, ID--OR","Homedale, ID", "Salmon, ID","Star, ID", "American Falls, ID", "Kellogg, ID", "Rigby, ID", "St. Maries, ID", "Lewiston, ID--WA", "Wendell, ID", "Blackfoot, ID", "Moscow, ID", "Orofino, ID", "Buhl, ID", "Soda Springs, ID", "Preston, ID", "Rathdrum, ID", "Emmett, ID", "Ketchum, ID", "Mountain Home AFB, ID", "Jerome, ID", "Kuna, ID", "Osburn, ID","Gooding, ID")

```

```{r}
il <- data |>
  filter(State == "IL")

unique(il$UA_NAME)

il_names <- c("Chicago, IL--IN", "Lawrenceville, IL","Peoria, IL", "Springfield, IL", "Decatur, IL", "Mount Vernon, IL", "Peru--LaSalle, IL", "Rockford, IL", "Mount Sterling, IL", "Champaign, IL", "Carbondale, IL", "Dixon, IL", "Bloomington--Normal, IL", "Clinton, IL",  "Freeport, IL", "Danville, IL", "Kankakee, IL", "Pittsfield, IL", "Princeton, IL", "Shelbyville, IL", "Robinson, IL", "Round Lake Beach--McHenry--Grayslake, IL--WI", "Rantoul, IL", "Carthage, IL", "St. Joseph, IL", "Taylorville, IL", "Pontiac, IL","Quincy, IL", "Macomb, IL", "Heyworth, IL", "Savanna, IL--IA", "Newton, IL", "Breese, IL", "Elmwood, IL", "Effingham, IL", "Mattoon, IL", "Carlinville, IL", "Steeleville, IL","Morris, IL", "Salem, IL", "Abingdon, IL", "Lincoln, IL", "Watseka, IL", "Bushnell, IL", "Waterloo, IL", "Mackinaw, IL", "Alton, IL--MO", "Chester, IL", "Nashville, IL" ,"Harrisburg, IL", "Red Bud, IL","Pana, IL","Mahomet, IL", "Sterling, IL", "Fairbury, IL", "Millstadt, IL" , "Galesburg, IL", "White Hall, IL", "Charleston, IL", "Centralia, IL", "Morrison, IL","Fairfield, IL", "West Frankfort, IL", "Braidwood--Coal City--Wilmington, IL", "DeKalb, IL", "Ottawa, IL", "Hillsboro, IL", "Vandalia, IL", "Pinckneyville, IL","Staunton, IL", "Paxton, IL", "Murphysboro, IL", "Paris, IL", "Rushville, IL","Jacksonville, IL", "Gillespie, IL", "Eureka, IL", "Eldorado, IL", "Aledo, IL", "Rochelle, IL", "Olney, IL" , "Christopher, IL", "Oregon, IL", "Geneseo, IL", "Mount Carmel, IL", "Canton, IL", "Hoopeston, IL", "Marengo, IL", "Monticello, IL", "Byron, IL", "Petersburg, IL", "Marshall, IL", "Lena, IL", "Metamora, IL", "Jerseyville, IL", "Du Quoin, IL", "Gilman, IL", "Litchfield, IL", "McLeansboro, IL", "Kewanee, IL", "Genoa, IL", "Beardstown, IL", "Mascoutah, IL", "Virden, IL","Smithton, IL","Carmi, IL","Peotone, IL","New Baden, IL", "Streator, IL", "Sullivan, IL", "Marseilles, IL", "Tuscola, IL", "Hampshire, IL", "Johnston City, IL","Sparta, IL","Auburn, IL","Metropolis, IL","Carlyle, IL","Greenville, IL","Woodstock, IL", "Momence, IL", "Monmouth, IL", "Bloomington, IN", "Gibson City, IL","Le Roy, IL", "Havana, IL", "Flora, IL", "Beecher, IL", "Mendota, IL","Highland, IL","Anna, IL", "Benton, IL", "Galena, IL","Harvard, IL","Nokomis, IL" , "Arcola, IL","Dwight, IL", "El Paso, IL","Casey, IL", "Lake Holiday, IL", "Pawnee, IL", "Mount Morris, IL", "Trenton, IL","Downs, IL","Cairo, IL","Davis Junction, IL")

```

```{r}
ind <- data |>
  filter(State == "IN")

unique(ind$UA_NAME)


in_names <- c("Richmond, IN--OH", "Lafayette, IN", "Indianapolis, IN", "Elkhart, IN--MI", "South Bend, IN--MI" , "Lebanon, IN", "Westville, IN", "Muncie, IN", "Connersville, IN", "Union City, IN--OH", "Marion, IN", "Fort Wayne, IN", "Kokomo, IN", "Greencastle, IN", "Scottsburg, IN", "Columbus, IN", "Cambridge City, IN", "Fort Branch, IN", "Hebron, IN", "Nappanee, IN", "Terre Haute, IN", "Covington, IN", "Elwood, IN", "Batesville, IN", "Bloomington, IN", "Kendallville, IN","Columbia City, IN","Michigan City--La Porte, IN--MI","Evansville, IN--KY","Anderson, IN","Crawfordsville, IN", "Huntington, IN", "Auburn, IN", "Wabash, IN", "Tipton, IN","Peru, IN", "Decatur, IN","Logansport, IN","Warsaw, IN","Fairmount, IN", "Plymouth, IN", "Charlestown, IN","Sheridan, IN","Vincennes, IN", "Angola, IN","Loogootee, IN", "Walkerton, IN","Monticello, IN", "Bloomfield, IN", "Portland, IN", "Martinsville, IN", "Bluffton, IN", "Greentown, IN", "Bremen, IN", "Tell City, IN--KY", "Greensburg, IN", "Rensselaer, IN", "Lagrange, IN", "Shelbyville, IN", "Lowell, IN", "Syracuse, IN", "Corydon, IN", "Oakland City, IN", "Jasper, IN", "Middlebury, IN", "Dunkirk, IN", "Salem, IN", "Hartford City, IN", "Paoli, IN", "Rockville, IN", "North Manchester, IN", "De Motte, IN", "Rushville, IN", "Berne, IN", "Winchester, IN", "Bedford, IN", "Delphi, IN", "Washington, IN", "Brownstown, IN", "Knightstown, IN",  "Knox, IN", "Seymour, IN", "Ossian, IN", "Madison, IN--KY", "North Webster, IN", "New Castle, IN", "Huntingburg, IN","Boonville, IN", "Lawrenceburg--Greendale--Aurora, IN", "Upland, IN",  "North Vernon, IN", "Linton, IN", "Middletown, IN", "Frankfort, IN", "Mount Vernon, IN" , "Rochester, IN", "Ligonier, IN",  "Attica, IN", "Bicknell, IN", "Princeton, IN", "Sullivan, IN", "Winamac, IN", "Mitchell, IN",  "Clinton, IN","New Carlisle, IN", "Butler, IN", "Grissom AFB, IN", "Heritage Lake, IN")

```

```{r}
ia <- data |>
  filter(State == "IA")

unique(ia$UA_NAME)

ia_names <- c("Des Moines, IA", "Osage, IA", "Rock Valley, IA", "Ames, IA", "Burlington, IA--IL", "Iowa City, IA", "Sioux City, IA--NE--SD", "Humboldt, IA", "Cedar Rapids, IA","De Witt, IA","Bellevue, IA",  "Estherville, IA", "Decorah, IA", "Clarinda, IA", "Carroll, IA", "Wilton, IA", "Indianola, IA", "Davenport, IA--IL", "Boone, IA", "Washington, IA", "Forest City, IA", "Waterloo, IA", "Albia, IA", "Shenandoah, IA", "Waukon, IA", "Waverly, IA", "Eagle Grove, IA", "Garner, IA", "Ottumwa, IA", "Sheldon, IA", "Dyersville, IA", "Clear Lake, IA", "Mount Vernon, IA", "Spencer, IA", "Muscatine, IA", "Pella, IA", "Dubuque, IA--IL", "Creston, IA", "Spirit Lake, IA", "Mount Pleasant, IA", "Nevada, IA", "Jefferson, IA", "Onawa, IA", "Fort Madison, IA--IL", "Newton, IA", "Cresco, IA", "Perry, IA", "Anamosa, IA", "Grinnell, IA", "Fort Dodge, IA", "West Liberty, IA", "Maquoketa, IA", "Clarion, IA", "Winterset, IA", "Algona, IA", "Story City, IA", "Oelwein, IA", "Denison, IA", "Keokuk, IA--IL", "Knoxville, IA", "Tama, IA", "Charles City, IA", "Marshalltown, IA", "Oskaloosa, IA", "Fairfield, IA", "Glenwood, IA", "Hampton, IA", "Tipton, IA", "Centerville, IA", "Red Oak, IA", "Osceola, IA", "Clinton, IA--IL", "Harlan, IA", "Huxley, IA", "Cherokee, IA", "Monticello, IA", "Mason City, IA", "Vinton, IA","Adel, IA","Storm Lake, IA","Webster City, IA", "Atlantic, IA", "Le Mars, IA", "Iowa Falls, IA", "Sioux Center, IA", "Independence, IA", "Manchester, IA", "Sibley, IA", "Orange City, IA", "Polk City, IA", "Chariton, IA","Carlisle, IA","Emmetsburg, IA", "Williamsburg, IA", "New Hampton, IA", "Missouri Valley, IA")
```


```{r}
ks <- data |>
  filter(State == "KS")

unique(ks$UA_NAME)

ks_names <- c("Kansas City, MO--KS", "Wichita, KS", "Topeka, KS", "Hays, KS", "Leavenworth, KS", "Pittsburg, KS", "Junction City, KS", "Manhattan, KS", "Scott City, KS", "El Dorado, KS", "Chanute, KS", "Atchison, KS--MO", "Hesston, KS","Dodge City, KS", "Garden City, KS","Lawrence, KS", "Great Bend, KS", "Clay Center, KS", "Baldwin City, KS", "Abilene, KS","Tonganoxie, KS", "Hiawatha, KS", "Wamego, KS", "Baxter Springs, KS", "Paola, KS", "McPherson, KS", "Liberal, KS", "Salina, KS", "Basehor, KS", "Girard, KS", "Russell, KS", "Lindsborg, KS", "Parsons, KS", "Wellington, KS", "Arkansas City, KS", "Larned, KS", "Hutchinson, KS", "Eudora, KS", "Independence, KS", "Ottawa, KS", "Kingman, KS", "Newton, KS", "Emporia, KS", "Colby, KS", "Hillsboro, KS", "Phillipsburg, KS", "Columbus, KS", "Concordia, KS", "Goodland, KS", "Marysville, KS", "Neodesha, KS", "Garnett, KS", "Augusta, KS", "Rose Hill, KS", "Iola, KS",  "Fort Scott, KS", "Beloit, KS", "Hugoton, KS", "Pratt, KS", "Winfield, KS", "Norton, KS", "Burlington, KS", "Lyons, KS", "Coffeyville, KS--OK", "Ulysses, KS", "Spring Hill, KS", "De Soto, KS", "Louisburg, KS", "Holton, KS", "Sabetha, KS", "Ellsworth, KS", "Eureka, KS", "Galena, KS--MO", "Osage City, KS", "Hoisington, KS", "Osawatomie, KS", "St. Marys, KS")


```

```{r}
ky <- data |>
  filter(State == "KY")

unique(ky$UA_NAME)

ky_names <- c("Bardstown, KY", "Benton, KY", "Louisville/Jefferson County, KY--IN", "London--Corbin, KY", "Maysville, KY--OH", "Paducah, KY--IL", "Elizabethtown--Radcliff, KY", "Russellville, KY", "Hopkinsville, KY", "Nicholasville, KY", "Hazard, KY", "Central City--Greenville, KY", "Middlesborough, KY--TN--VA", "Murray, KY", "Lexington-Fayette, KY", "Frankfort, KY", "Louisa, KY--WV", "Bowling Green, KY", "Evarts, KY", "Georgetown, KY", "Danville, KY", "Madisonville, KY", "Scottsville, KY", "Winchester, KY", "Owensboro, KY", "Prestonsburg, KY", "Richmond, KY", "Cynthiana, KY", "Lebanon, KY", "Berea, KY", "Pikeville, KY", "Williamsburg, KY","Flemingsburg, KY", "Shelbyville, KY", "Williamstown, KY", "Harrodsburg, KY", "Paintsville, KY", "Lancaster, KY", "Morganfield, KY", "Mayfield, KY", "Glasgow, KY", "Princeton, KY", "Stanford, KY",  "Cumberland, KY", "Jackson, KY", "Somerset, KY", "Morehead, KY", "Carrollton, KY", "Columbia, KY", "Fulton, KY--TN", "Campbellsville, KY", "Barbourville, KY", "Mount Sterling, KY", "Manchester, KY", "Monticello, KY", "Lawrenceburg, KY", "Leitchfield, KY", "Wilmore, KY", "Beaver Dam, KY", "Marion, KY", "Paris, KY", "Versailles, KY", "Harlan, KY", "Franklin, KY", "Grayson, KY", "Stanton, KY", "Hodgenville, KY" ,"Horse Cave, KY", "Mount Vernon, KY", "Irvine, KY", "Crittenden, KY", "Cadiz, KY")

```

```{r}
la <- data |>
  filter(State == "LA")

unique(la$UA_NAME)

la_names <- c("Lafayette, LA", "Baton Rouge, LA", "Shreveport, LA", "Houma, LA", "New Orleans, LA", "Lake Charles, LA", "Natchitoches, LA", "DeRidder, LA", "Hammond, LA", "Crowley, LA", "Slidell, LA", "Monroe, LA", "Bogalusa, LA", "Mandeville--Covington, LA", "Amite City, LA", "Bastrop, LA", "Galliano--Larose--Cut Off, LA", "Breaux Bridge, LA", "Opelousas, LA", "Vinton, LA", "Alexandria, LA", "St. Martinville, LA", "Leesville, LA" , "Eunice, LA", "Fort Polk, LA", "Oakdale, LA", "Delhi, LA", "Jeanerette, LA", "Abbeville, LA", "Jennings, LA", "New Roads, LA", "Gramercy--Lutcher, LA", "Farmerville, LA", "Minden, LA", "Iowa, LA", "Pierre Part, LA", "Benton, LA", "Sunset, LA", "Donaldsonville, LA", "DeQuincy, LA", "Ruston, LA",  "Marksville, LA", "Morgan City, LA", "Tallulah, LA", "Cottonport, LA", "Jean Lafitte, LA", "Winnfield, LA" , "Franklinton, LA", "Port Barre, LA", "Livonia, LA", "Vivian, LA", "Springhill, LA", "Winnsboro, LA", "Homer, LA","Jena, LA", "Bunkie, LA", "Arcadia, LA", "Franklin, LA", "Welsh, LA", "Many, LA", "Church Point, LA", "Mansfield, LA", "Jonesboro, LA", "Rayville, LA", "Kaplan, LA", "Rayne, LA", "Ville Platte, LA", "Ferriday, LA", "Lake Arthur, LA", "Lake Providence, LA", "Buras, LA", "Mamou, LA")

```

```{r}
me <- data |>
  filter(State == "ME")

unique(me$UA_NAME)

me_names <- c("Lewiston, ME", "Waterville, ME", "Camden, ME",  "Portland, ME", "Bangor, ME" , "Calais, ME", "Ellsworth, ME", "Belfast, ME", "Augusta, ME", "Brunswick, ME", "Houlton, ME", "Presque Isle, ME", "Skowhegan, ME", "Bar Harbor, ME", "Millinocket, ME", "Sanford, ME",  "Caribou, ME",  "Rumford, ME", "Livermore Falls, ME", "Rockland, ME", "Pittsfield, ME", "South Paris, ME", "Kennebunk, ME", "Farmington, ME")


```

```{r}
md <- data |>
  filter(State == "MD")

unique(md$UA_NAME)

md_names <- c("Baltimore, MD", "Ocean Pines, MD--DE", "Lexington Park--California--Chesapeake Ranch Estates, MD",  "Hagerstown, MD--WV--PA", "Westminster--Eldersburg, MD", "Mountain Lake Park, MD", "Cambridge, MD", "Waldorf, MD", "Crisfield, MD", "Aberdeen--Bel Air South--Bel Air North, MD", "Easton, MD", "Salisbury, MD--DE", "Thurmont, MD", "Frederick, MD", "Leonardtown, MD", "Prince Frederick, MD", "Emmitsburg, MD--PA", "Cumberland, MD--WV--PA", "Taneytown, MD", "Chestertown, MD", "Federalsburg, MD", "Westernport, MD--WV", "Glenwood, MD", "Shady Side--Deale, MD", "Denton, MD", "Princess Anne, MD", "Brunswick, MD--VA", "Chesapeake Beach, MD", "Poolesville, MD","Pocomoke City, MD","Centreville, MD", "Manchester, MD", "Long Beach, MD", "Romancoke, MD")

```

```{r}
ma <- data |>
  filter(State == "MA")

unique(ma$UA_NAME)

ma_names <- c("Springfield, MA--CT", "Worcester, MA--CT", "Boston, MA--NH--RI", "Barnstable Town, MA", "New Bedford, MA", "Pittsfield, MA", "Leominster--Fitchburg, MA", "South Deerfield, MA", "Ware, MA", "Lee, MA", "Great Barrington, MA", "Greenfield, MA", "North Adams, MA--VT", "North Brookfield, MA", "Athol, MA", "Vineyard Haven, MA", "Provincetown, MA", "Nantucket, MA")

```

```{r}
mi <- data |>
  filter(State == "MI")

unique(mi$UA_NAME)

mi_names <- c("Detroit, MI", "Port Huron, MI", "Grand Rapids, MI", "Ann Arbor, MI", "Fowlerville, MI", "Jackson, MI", "Alpena, MI", "Kalamazoo, MI", "Flint, MI", "Traverse City, MI", "Sturgis, MI", "Lansing, MI", "Lapeer, MI" ,"Bay City, MI", "Big Rapids, MI", "Muskegon, MI", "Iron River, MI", "South Haven, MI", "Frankenmuth, MI", "Saginaw, MI", "Benton Harbor--St. Joseph--Fair Plain, MI", "Mount Pleasant, MI", "Houghton Lake, MI", "Hastings, MI", "Escanaba, MI", "Monroe, MI", "Midland, MI", "South Lyon--Howell, MI", "Munising, MI","Belding, MI", "Dorr, MI", "Three Rivers, MI", "Marshall, MI", "Chelsea, MI","Williamston, MI","Clare, MI","Sault Ste. Marie, MI", "Coldwater, MI", "Holland, MI", "Milan, MI", "East Tawas, MI","Marquette, MI", "Charlevoix, MI", "Grayling, MI","Hart, MI","Gladwin, MI","Houghton, MI", "Paw Paw Lake--Hartford, MI","Goodrich, MI", "Battle Creek, MI", "Allegan, MI", "Adrian, MI", "Bad Axe, MI", "Eaton Rapids, MI", "Ionia, MI", "Otsego--Plainwell, MI", "Imlay City, MI", "Gaylord, MI", "Kalkaska, MI", "Ironwood, MI--WI", "Paw Paw, MI","Greenville, MI", "Cheboygan, MI", "Harrison, MI", "Charlotte, MI","Sparta, MI", "Petoskey, MI" ,"Manistique, MI", "Albion, MI","Durand, MI", "Hillsdale, MI", "Berrien Springs, MI", "Brooklyn, MI", "Dowagiac, MI", "Vassar, MI", "Caro, MI", "Perry, MI","Owosso, MI", "Newberry, MI","Whitehall, MI", "Ishpeming, MI","Richmond, MI","Almont, MI","Newaygo, MI", "Portland, MI", "Manistee, MI", "Douglas, MI", "Cadillac, MI", "Laurium, MI", "Iron Mountain--Kingsford, MI--WI", "Dundee, MI", "Alma--St. Louis, MI", "St. Johns, MI", "Middleville, MI", "Blissfield, MI", "Constantine, MI", "Au Sable, MI", "St. Ignace, MI", "Holly, MI", "Fremont, MI", "Boyne City, MI", "Coopersville, MI", "Wayland, MI", "Rogers City, MI", "Lowell, MI", "Ludington, MI","Sandusky, MI", "Gun Lake, MI", "Kinross, MI", "Cedar Springs, MI", "Somerset, MI")
```

```{r}
mn <- data |>
  filter(State == "MN")

unique(mn$UA_NAME)

mn_names <- c("Minneapolis--St. Paul, MN--WI","Delano, MN","Le Sueur, MN", "Norwood Young America, MN","Rochester, MN","Virginia, MN","Waseca, MN","Monticello--Big Lake, MN","Brainerd, MN", "Faribault, MN","Winona, MN", "St. Cloud, MN", "St. Francis, MN", "Annandale, MN","Cambridge, MN","Pine Island, MN", "Crookston, MN", "Grand Rapids, MN", "Litchfield, MN", "Fergus Falls, MN", "Morris, MN",  "Hibbing, MN", "Mora, MN", "Two Harbors, MN",  "Duluth, MN--WI","Perham, MN", "St. James, MN", "Belle Plaine, MN", "Hutchinson, MN", "Stewartville, MN", "Marshall, MN","Jackson, MN","Long Prairie, MN","Mankato, MN","Waconia, MN","Windom, MN","Fairmont, MN","Wadena, MN","Albert Lea, MN","Cloquet, MN","Northfield, MN", "Bemidji, MN", "Cannon Falls, MN","Dodge Center, MN", "Montgomery, MN", "Buffalo, MN","Cokato, MN","Redwood Falls, MN","Pipestone, MN","Park Rapids, MN", "International Falls, MN", "Zimmerman, MN", "Owatonna, MN","Lake City, MN", "Cold Spring, MN", "Little Falls, MN", "Forest Lake, MN", "Hastings, MN","New Ulm, MN", "Chisholm, MN","Luverne, MN","Granite Falls, MN", "Becker, MN", "St. Charles, MN","Pine City, MN","Austin, MN", "St. Peter, MN","Alexandria, MN", "New Prague, MN", "Sauk Centre, MN","Red Wing, MN","Zumbrota, MN", "Thief River Falls, MN",  "Roseau, MN", "Kasson, MN","Lindstrom--Chisago City, MN","Plainview, MN", "Crosby, MN","Worthington, MN", "Sleepy Eye, MN","North Branch, MN","Princeton, MN", "Willmar, MN", "Chatfield, MN", "Benson, MN", "Detroit Lakes, MN", "Ely, MN",  "Watertown, MN","Melrose, MN",  "Caledonia, MN", "Staples, MN", "Lonsdale, MN", "Byron, MN", "Moose Lake, MN", "Montevideo, MN", "Jordan, MN", "Glencoe, MN","Rush City, MN","Montrose, MN","Rockford, MN", "Elko New Market, MN" , "Lake Crystal, MN", "Albany, MN", "New London, MN","Milaca, MN","Blue Earth, MN")

```





```{r, include = FALSE}
data_not_college_town <- data |>
  filter(college_town == 0)

non_college_towns <- as.tibble(unique(data_not_college_town$UA_NAME))
non_college_towns

```
```{r}
coffee_data <- data |>
  filter(RestaurantName %in% c("Dunkin", "Starbucks")) 
```

```{r}
pop_towns <- c("Huntsville, AL", "Birmingham, AL", "Montgomery, AL", "MObile, AL", "Tuscaloosa, AL",
               
               "Anchorage, AK", "Fairbanks, AK", "Juneau, AK", "Wasilla, AK", "Sitka, AK",
               
               "Phoenix--Mesa, AZ", "Tuscon, AZ", "Chandler, AZ", "Gilbert, AZ",
               
               "Little Rock, AR", "Fayetteville--Springdale--Rogers, AR--MO", "Fort Smith, AR--OK", "Jonesboro, AR",
               
               "Los Angeles--Long Beach--Anaheim, CA", "San Diego, CA", "San Jose, CA", "Fresno, CA", "San Francisco--Oakland, CA",
               
               "Carbonate, CO", "Denver--Aurora, CO", "Colorado Springs, CO", "Fort Collins, CO",
               
               "Bridgeport--Stamford, CT", "New Haven, CT", "Hartford, CT", "Waterbury, CT",
               
               "Wilmington, DE", "Dover, DE", "Newark, DE", "Middletown, DE", "Smyrna, DE",
               
               "Washington, DC--VA--MD", 
               
               "Jacksonville, FL", "Miami, FL", "Tampa--St.Petersburg, FL", "Orlando, FL",
               
               "Atlanta, GA", "Columbus, GA--AL", "Augusta-Richmond County, GA--SC", "Macon, GA", "Savannah, GA",
               
               "Urban Honolulu, HI",
               
               "Boise City, ID", "Meridian, ID", "Nampa, ID", "Idaho Falls, ID", "Caldwell, ID",
               
               "Chicago, IL--IN", "Aurora, IL", "Joliet, IL", "Naperville, IL", "Rockford, IL", 
               
               "Indianapolis, IN", "Fort Wayne, IN", "Evansville, IN", "South Bend, IN--MI", "Carmel, IN",
               
               "Des Moines, IA", "Cedar Rapids, IA", "Davenport, IA--IN", "Sioux City, IA--NE--SD", "Iowa City, IA",
               
               "Wichita, KS", "Overland Park, KS", "Kansas City, MO--KS", "Olathe, KS", "Topeka, KS",
               
               "Louisville/Jefferson County, KY--IN", "Lexington-Fayette, KY", "Bowling Green, KY", "Owensboro, KY", "Convington, KY",
               
               "New Orleans, LA", "Baton Rouge, LA", "Shreveport, LA", "Lafayette, LA", "Lake Charles, LA",
               
               "Portland, ME", "Lewiston, ME", "Bangor, ME", "South Portland, ME", "Auburn, ME",
               
               "Baltimore, MD", "Frederick, MD", "Gaithersburg, MD", "Rockville, MD", "Bowie, MD",
               
               "Boston, MA--NH--RI", "Worcester, MA--CT", "Springfield, MA--CT", "Cambridge, MA", "Lowell, MA", 
               
               "Detroit, MI", "Grand Rapids, MI", "Warren, MI", "Sterling Heights, MI", "Ann Arbor, MI", 
               
               "Minneapolis--St.Paul, MN--WI", "Rochester, MN", "Bloomington, MN", "Brooklyn Park, MN",
               
               "Jackson, MS", "Gulfport, MS", "Southhaven, MS", "Biloxi, MS", "Hattiesburg, MS",
               
               "St.Louis, MO--IL", "Springfield, MO", "Columbia, MO", "Independence, MO",
               
               "Billings, MT", "Missoula, MT", "Great Falls, MT", "Bozeman, MT", "Butte-Silver Bow, MT",
               
               "Omaha, NE", "Lincoln, NE", "Bellevue, NE", "Grand Island, NE", "Kearney, NE",
               
               "Las Vegas--Henderson, NV", "Reno, NV-CA", "Sparks, NV", "Carson City, NV",
               
               "Manchester, NH", "Nashua, NH--MA", "Concord, NH", "Dover--Rochester, NH--ME", 
               
               "New York--Newark, NY--NJ--CT", "Jersey City, NJ", "Paterson, NJ", "Elizabeth, NJ", "Trenton, NJ",
               
               "Alburquerque, NM", "Las Cruces, NM", "Rio Rancho, NM", "Santa Fe, NM", "Roswell, NM",
               
               "Buffalo, NY", "Yonkers, NY", "Rochester, NY", "Syracuse, NY",
               
               "Charlotte, NC--SC", "Raleigh, NC", "Greensboro, NC", "Durham, NC", "Winston-Salem, NC",
               
               "Fargo, ND--MN", "Bismarck, ND", "Grand Forks, ND--MN", "Minot, ND", "Williston, ND", 
               
               "Columbus, OH", "Cleveland, OH", "Cincinnati, OH--KY--IN", "Toledo, OH--MI", "Akron, OH",
               
               "Okalahoma City, OK", "Tulsa, OK", "Norman, OK", "Broken Arrow, OK", "Edmond, OK",
               
               "Portland, OR--WA", "Salem, OR", "Eugene, OR", "Gresham, OR", "Hillsboro, OR",
               
               "Philadelphia, PA--NJ--DE--MD", "Pittsburgh, PA", "Allentown, PA--NJ", "Reading, PA", "Erie, PA",
               
               "Providence, RI--MA", "Warwich, RI", "Cranston, RI", "Pawtucket, RI", "Woonsocket, RI",
               
               "Charleston--North Charleston, SC", "Columbia, SC", "Mount Pleasant, SC", "Rock Hill, SC", "Greenville, SC",
               
               "Sioux Falls, SD", "Rapid City, SD", "Aberdeen, SD", "Brookings, SD", "Watertown, SD",
               
               "Nashville-Davidson, TN", "Memphis, TN--MS--AR", "Knoxville, TN", "Chattanooga, TN--GA", "Clarksville, TN--KY",
               
               "Houston, TX", "San Antonio, TX", "Dallas--Fort Worth--Arlington, TX", "Austin, TX",
               
               "Salt Lake City--West Valley City, UT", "West Jordan, UT", "Provo-Orem, UT",
               
               "Burlington, VT", "Rutland, VT", "Essex Junction, VT", "Barre--Montpelier, VT",
               
               "Virginia Beach, VA", "Chesapeake, VA", "Norfolk, VA", "Richmond, VA", "Newport News, VA",
               
               "Seattle, WA", "Spokane, WA", "Tacoma, WA", "Vancouver, WA", "Bellevue, WA",
               
               "Charleston, WV", "Huntington, WV--KY--OH", "Parkersburg, WV--OH", "Morgantown, WV", "Wheeling, WV--OH", 
               
               "Milwaukee, WI", "Madison, WI", "Green Bay, WI", "Kenosha, WI--IL", "Racine, WI",
               
               "Cheyenne, WY", "Casper, WY", "Gillette, WY", "Laramie, WY", "Rock Springs, WY")

```

```{r}
data |>
  mutate(is_pop = if_else(UA_NAME %in% pop_towns, "Yes", "No"))

```
## First Data Visualization

```{r}
coffee_data |>
  mutate(college_town_new = if_else(college_town == 1, "College Town", "Non-College Town"),
         `Restaurant Name` = if_else(RestaurantName == "Dunkin", "Dunkin' Donuts", "Starbucks")) |>
  ggplot(mapping = aes(x = college_town_new, fill = `Restaurant Name`)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = c("salmon", "palegreen4")) +
  labs(title = "Chain Coffee Locations and College Towns", y = "Count of Locations", x = "")


```
## Analysis 1

Of the sampled Dunkin' Donuts and Starbucks locations, there appears to be a correlation between location of restaurants and college towns. The following table calculates the percentage of sampled Dunkin' Donuts and Starbucks locations that are located in college towns as opposed to non-college towns. Additionally, the average treatment effect of the town being a college town as opposed to a non-college town is calculated as the Average Treatment Effect.  

```{r}
props <- coffee_data |>
  mutate(new_name = if_else(RestaurantName == "Dunkin", "Dunkin' Donuts", "Starbucks")) |>
  group_by(new_name, college_town) |>
  summarize(count = n()) |>
  pivot_wider(names_from = college_town, values_from = count) |>
  mutate(perc_college_town = (`1`/(`1` + `0`)) * 100,
         perc_non_college_town = (`0`/(`1` + `0`)) * 100,
         ate = perc_college_town - perc_non_college_town) 

props |>
  select(perc_college_town, perc_non_college_town, ate) |>
  knitr :: kable(caption = "Percent of Sampled Chain Coffee Locations in College versus Non-College Towns", col.names = c("Restaurant Name", "College Town (%)", "Non-College Town (%)", "Average Treatment Effect (%)"), digits = 2)

```

These results suggest that there is a fairly substansive difference between the percent of Dunkin' Donuts and Starbucks locations that are located in college towns as opposed to non-college towns. There are approximately 61% more Dunkin' Donuts locations in college towns and that number grows to nearly 65% for Starbucks. 

## Analysis 2

```{r}
data <- data |>
  mutate(is_chain_coffee = if_else(RestaurantName %in% c("Dunkin", "Starbucks"), "Yes", "No"))

data |>
  filter(is_chain_coffee == "Yes") |>
  group_by(college_town) |>
  summarize(n = n()) |>
  pivot_wider(names_from = college_town, values_from = n) |>
  mutate(ate = `1` - `0`,
         ate_perc = ate/(`1` + `0`))


```


```{r, eval = FALSE, echo = FALSE} 

non_college_coffee_data <- data_not_college_town |>
  filter(RestaurantName %in% c("Dunkin", "Starbucks"))

non_tibble <- as.tibble(unique(non_college_coffee_data$UA_NAME))

nrow(non_college_towns) - nrow(non_tibble)

c <- data |>
  filter(college_town == 1)

college_coffee_data <- coffee_data |>
  filter(college_town ==1)

col_town_tibble <- as.tibble(unique(c$UA_NAME))

col_tibble <- as.tibble(unique(college_coffee_data$UA_NAME))


nrow(col_town_tibble) - nrow(col_tibble)

```













